### 2022-11-06 main.tex
inital commit, adding overleaf code and refactored google collab code

\documentclass[12pt]{article}
\usepackage[paper=letterpaper,margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{newtxtext, newtxmath}
\usepackage{enumitem}
\usepackage{titling}
\usepackage[colorlinks=true]{hyperref}

\setlength{\droptitle}{-6em}

% Enter the specific assignment number and topic of that assignment below, and replace "Your Name" with your actual name.

\begin{document}
\begin{enumerate}[leftmargin=\labelsep]
\item[8.]

\item[9.]
    \begin{enumerate}
        \item 
        let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
        Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:

        $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) \ge 0$
        We expand our kernel function to give: \\

        \[\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) =  \sum_{n,m} cu_{n} u_{m} + \sum_{n,m} \langle\textbf{x}_{n}, \textbf{x}_{m}\rangle u_{n} u_{m}\]

        Here, we note that $\langle \cdot, \cdot \rangle$ is an inner product over the Hilbert space $\mathcal{R}^{n}$ and hence is psd by the representer theorem:
                \begin{equation}
        \implies \sum_{n,m} \langle\textbf{x}_{n},
        \textbf{x}_{m}\rangle u_{n} u_{m} \ge 0 
                \end{equation}

        \textbf{Proposition}

        $K_{c}(\cdot, \cdot)$ is psd iff $c \ge0$

        \textbf{Proof:}\\
        $(\implies)$\\

        Suppose $c \ge 0$.

         $(1) \implies \sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) \ge c \sum_{n,m}u_{n}u_{m} = c (\sum_{n}u_{n})^{2} \ge 0$\\

        $(\impliedby)$\\

        let $c < 0$.
        Suppose our vectors $x_{n}$ are identically equal to $ (\sqrt{a},0)^{T}$, for some $a < |c|/n \implies x_{k}^{T}x_{l} = a $\\
        $\forall k,l$.\\

        $\implies \sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) = (a+c) \sum_{n,m}u_{n}u_{m} = (a + c)(\sum_{n}u_{n})^{2} < 0$\\
        Hence for any $c < 0$, $
        \exists \{ u_{i} \}_{1:m} \in \mathcal{R},
         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$s.t:\\
           $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) < 0
        \square$
    \item
    Using this kernel in our ridge regression, we arrive at the following prediction function:
    \\
    \[\hat{y}_{test} = lc + \sum_{i} \alpha_{i} x_{i} \cdot x_{test} \]

    where $\mathbf{\alpha} = ( K + \gamma l I_{l} + c 1_{nxn}) ^{-1} y_{train}$\\
    Where $1_{nxn}$ is a matrix of all ones.\\

    We note that as c becomes large, $\alpha \to 0$ and hence the predictions for $\hat{y}_{test}$ approach    
    the constant function $f(x) = lc$
    \\
    \newpage

    \item
    Define $g(t) := $sgn$(f(t)) = \frac{f(t)}{| f(t)|}$\\
    \textbf{Proposition:}\\

    as $\beta \to \infty$, $g(t) \to 1-NN$\\

    \textbf{Proof:}\\

    $f(t) = \sum_{i} \alpha_{i} K(x_{i}, t)$, where $ \alpha = (K + \gamma I_{l})^{-1} y$\\

    since $K(x,x) = exp(0) = 1$ for  all x, we decompose K as follows:\\

    $K = I_{l} + \tilde{K}$, where $\tilde{K}_{ij} = K(x_i, x_j)$, $i \ne j$. We note here that as $\beta \to \infty$, $ \tilde{K} \to 0$.\\

    We take a taylor expansion in $\tilde{K}$, to arrive at the following result:\\

    $\alpha = ((\gamma+1) I_{l} + \tilde{K})^{-1} y = \frac{1}{\gamma + 1} (I_{l} - O(\tilde{K})) y $
    Hence as $\beta \to \infty$, $\alpha \to \frac{1}{\gamma +1}y$\\
    Hence our predictor function becomes:\\
    $f(t) \to \frac{1}{\gamma+1} \sum_{i} y_{i} K(x_{i}, t) \implies g(t)  \to \frac{\sum_{i} y_{i} K(x_{i}, t)}{|\sum_{i} y_{i} K(x_{i}, t)|}
    $\\

    Let's assume that there exists a unique point x in our training set of minimal distance to our test point.\\

    Define $d_{i} := \|x_{test} - x_{i}\|^{2}$, and $d* := min_{i} d_{i}$\\
    \\
    $g(t) = \frac{y_{*} exp(-\beta d_{*})}{|\sum_{i} y_{i} exp(-\beta d_{i})|} + \sum_{i\ne *}\frac{y_{i} exp(-\beta d_{i})}{|\sum_{i} y_{i} exp(-\beta 
    d_{i})|} = \frac{y_{*}}{|y_{*} + \sum_{i \ne *} y_{i} exp(-\beta (d_{i} - d_{*}))|} + \sum_{i\ne *}\frac{y_{i} exp(-\beta (d_{i} - d_{*}))}{|y_{*} + \sum_{i \ne *} y_{i} exp(-\beta (d_{i} - d_{*}))|}$.\\

    Note for $d_{i} \ne d_{*}$, $exp(-\beta(d_{i} - d_{*})) \to 0$ as $\beta \to \infty$. Hence:\\
    $g(t) \to \frac{y_{*}}{|y_{*} + 0|} + \frac{0}{|y_{*} + 0|} = y_{*} = y_{i} : x_{i} = min_{i} \|x_{test} - x_{i}\|$ which is the required 1-NN predictor.\\$
    \square$
    \item
    Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen. We first index all permissible moves by $T_{i,j}$, which has the effect of flipping the state of squares $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, as long as each coordinate is still on the grid.\\
    We may consider each grid as an element of the space of square matrices over $\mathcal{F}_{2}$, the finite field of order 2: under this construction, we see that the application of a move $T_{i,j}$ corresponds to the sum between the grid and a matrix $T_{ij}$, where $T_{ij}$, where the entries of $T_{ij}$ are zero everywhere except at $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, if these values are present on the grid. For example, if n = 4, the transformation $T_{2,2}$ corresponds to the addition of the matrix $T_{22}$:\\

   $T_{22} = $ \begin{pmatrix}
    0 & 1 & 0 & 0\\
    1 & 1 & 1 & 0\\
    0 & 1 & 0 & 0\\
    0 & 0 & 0 & 0\\
    \end{pmatrix}
    \\
    Since our operations on a grid are now simply the sum of matrices over a $\mathcal{F}_{2}$, it is now immediately obvious that our operations are commutative, by the commutativity of addition.\\

    Further, since applying the same operation twice would be the same as applying the matrix twice in order, we can see that any operation applied twice would have the effect of applying no operation at all ( since $T_{ij} + T_{ij} = 0)$.\\
    Hence, we conclude for $1 \le i,j \le n$, each operation is applied at most once. From this point, we note that there is no reason for our operations to be square matrices, as the only required properties of the space are those of a vector space (we make no use here of matrix multiplication). Hence, we may vectorise both our input grid and our operation matrices to get a set of vectors over $F_{2}^{n^2}$. We now index our operation vectors $t_i: i = 1, \dots, n^2$.\\
    Let $x_{i} = \mathcal{I} [t_{i} $ is used $]$ be an indicator function representing whether $t_i$ is added to the input to get our blank grid.\\
    We observe that our problem is solvable for a given input grid G (now vectorised as a vector \textbf{g}) iff there exists a vector \textbf{x} $\in \mathrm{F}_{2}^{n^2}$ st:\\
    $\sum_{i} t_{i} x_{i} + \mathbf{g} = \mathbf{0}.$\\
    If we stack the vectors $t_{i}$ horizontally as the columns of a matrix T, we get:\\
    $T\mathbf{x} + \mathbf{g} = 0$\\
    Since every element is its own additive inverse over $\mathcal{F}_{2}$, we add $\mathbf{g}$ to both sides and arrive at the linear system $T \mathbf{x} = \mathbf{g}$.\\
    Since the matrix T may not be invertible in general, we perform gaussian elimination over $\mathcal{F}_{2}$, i.e create an augmented matrix $[T|\mathbf{g}]$ and reduce to row echelon form. If the problem is solvable, we will end up with a consistent (but perhaps underdetermined) reduced system of equations. If the input has no solution, the reduced system of equations will have some inconsistency in its variables: there will be some row of the reduced row echelon augmented matrix with all zeros to the left of the augmentation line, and a non-zero entry to the right of the augmentation line. \\

    Finally, we make a note of the time complexity of this algorithm: the creation of our matrix T can be performed in $O(n^{4})$ since we have $n^2$ operation grids of size $n^{2}$. Further, gaussian elimination can be performed in $O(n^{3})$ operations in any field, and hence our total running time is $O(n^3)$. \\

    Once we have determined whether a grid configuration is solvable, it remains to find a valid solution. We note that if a solution exists, then a least squares solver should find it. This operation should take $O(n^3)$ operations.

    \end{enumerate}
\item

\end{enumerate}
\end{document}

### 2022-11-06 main.py

@@ -1,0 +1,221 @@
+import os
+
+import numpy as np
+import pandas as pd
+
+from src.constants import OUTPUTS_FOLDER
+from src.models.helpers import phi_polynomial, phi_sin, train_test_split
+from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
+
+if __name__ == "__main__":
+    if not os.path.exists(OUTPUTS_FOLDER):
+        os.makedirs(OUTPUTS_FOLDER)
+
+    # Question 1
+    Q1_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q1")
+    if not os.path.exists(Q1_OUTPUT_FOLDER):
+        os.makedirs(Q1_OUTPUT_FOLDER)
+
+    x = np.array([1, 2, 3, 4]).reshape(-1, 1)
+    y = np.array([3, 2, 0, 5]).reshape(-1, 1)
+    ks = [1, 2, 3, 4]
+    q1.a(
+        x,
+        y,
+        ks,
+        figure_title="Question 1a: Regression",
+        figure_path=os.path.join(Q1_OUTPUT_FOLDER, "q1a.png"),
+    )
+    q1.b(x, y, ks, table_path=os.path.join(Q1_OUTPUT_FOLDER, "q1b.csv"))
+    q1.c(x, y, ks, table_path=os.path.join(Q1_OUTPUT_FOLDER, "q1c.csv"))
+
+    # Question 2
+    Q2_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q2")
+    if not os.path.exists(Q2_OUTPUT_FOLDER):
+        os.makedirs(Q2_OUTPUT_FOLDER)
+    number_of_sample_points = 30
+    sigma = 0.07
+    ks = np.array([2, 5, 10, 14, 18])
+    q2_and_3.a_i(
+        number_of_sample_points,
+        sigma,
+        figure_title="Question 2ai: Noisy Samples",
+        figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2ai.png"),
+    )
+    q2_and_3.a_ii(
+        number_of_sample_points,
+        sigma,
+        ks,
+        figure_title="Question 2aii: Regression with Polynomial Basis",
+        figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2aii.png"),
+    )
+    q2_and_3.b(
+        number_of_sample_points,
+        sigma,
[…]

### 2022-11-06 src/constants.py

@@ -1,0 +1,2 @@
+OUTPUTS_FOLDER = "outputs/python"
+DEFAULT_SEED = 0

### 2022-11-06 src/models/helpers.py

@@ -1,0 +1,25 @@
+import numpy as np
+
+
+def least_square_solution(x: np.ndarray, y: np.ndarray) -> np.ndarray:
+    return np.linalg.solve(x.T @ x, x.T @ y)
+
+
+def phi_polynomial(x: np.ndarray, k: int):
+    return np.concatenate([x**i for i in range(k - 1, -1, -1)], axis=1)
+
+
+def phi_sin(x: np.ndarray, k: int):
+    return np.concatenate([np.sin(i * np.pi * x) for i in range(k, 0, -1)], axis=1)
+
+
+def mean_squared_error(y_actual: np.ndarray, y_predicted: np.ndarray):
+    return np.mean((y_actual - y_predicted) ** 2)
+
+
+def train_test_split(x, y, split):
+    n = x.shape[0]
+    indices = np.random.choice(range(n), int(split * n))
+    mask = np.ones(n, dtype=bool)
+    mask[indices] = False
+    return x[indices, :], y[indices], x[mask, :], y[mask]

### 2022-11-06 src/models/knn.py

@@ -1,0 +1,124 @@
+from typing import Tuple
+
+import numpy as np
+
+from src.constants import DEFAULT_SEED
+
+
+def get_p_h(
+    number_of_points: int, n_dims: int, seed: int = DEFAULT_SEED
+) -> Tuple[np.ndarray, np.ndarray]:
+    """
+    generate data for a voted-center hypothesis
+    """
+    np.random.seed(seed)
+    x = np.random.uniform(low=0, high=1, size=(number_of_points, n_dims))
+    y = np.random.choice(a=[0, 1], size=number_of_points)
+    return x, y
+
+
+def _all_distances(a, b):
+    """
+    a is (N, D)
+    b is (M, D)
+    returns all euclidean norm distances between a and b (N, M)
+
+    """
+
+    return np.sqrt(((a.T[:, None] - b.T[:, :, None]) ** 2).sum(0)).T
+
+
+def knn_prediction(
+    train_data: Tuple[np.ndarray, np.ndarray], test_points: np.ndarray, k: int
+) -> np.ndarray:
+    """
+    Make knn prediction on test_points using train_data
+
+    train_data: Tuple of x, y for training
+    test_points: numpy array of test points
+    k: an integer
+
+    return label for each test point
+    """
+    train_x, train_y = train_data
+    euclidean_distances = _all_distances(test_points, train_x)
+    sorted_euclidean_distance_idxs = np.argsort(euclidean_distances, axis=1)
+    k_closest_idxs = sorted_euclidean_distance_idxs[:, :k]
+
+    vote_percentages = np.sum(train_y[k_closest_idxs], axis=1) / k
+
+    # find_undefined cases and choose randomly
+    idx_undefined = np.where(vote_percentages == 0.5)[0]
+    vote_percentages[idx_undefined] = np.random.choice(
+        a=[0, 1], size=len(idx_undefined)
+    )
+
+    # choose label
+    vote = np.round(vote_percentages)
+    return vote
+
+
+def _noisy_knn_prediction(
+    train_data: Tuple[np.ndarray, np.ndarray], test_points: np.ndarray, k: int
+) -> np.ndarray:
+    """
+    do knn but randomly choose label 20% of the time
+    """
+    # flip coin
+    coin_flip = np.random.choice(
+        a=[0, 1], size=len(test_points), p=[0.2, 0.8]
+    )  # 0 is tails, 1 is head
+
+    # use knn to generate label
+    labels = knn_prediction(train_data, test_points, k)
+
[…]

### 2022-11-06 src/models/regression_models.py

@@ -1,0 +1,101 @@
+from abc import ABC, abstractmethod
+
+import jax.numpy as jnp
+import numpy as np
+from jax import vmap
+
+from src.models.helpers import least_square_solution
+
+
+class RegressionModel(ABC):
+    def __init__(self):
+        self.coefficients = None
+        self.x_train = None
+
+    @abstractmethod
+    def fit(self, x_train, y_train):
+        raise NotImplementedError("Please Implement this method")
+
+    @abstractmethod
+    def predict(self, x_test):
+        raise NotImplementedError("Please Implement this method")
+
+    def fit_predict(self, x_train, y_train, x_test):
+        self.fit(x_train, y_train)
+        return self.predict(x_test)
+
+    def reset(self):
+        self.coefficients = None
+        self.x_train = None
+
+    @staticmethod
+    def add_ones(X):
+        return np.c_[np.ones(X.shape[0]), X]
+
+
+class NaiveLinearRegression(RegressionModel):
+    def __init__(self):
+        self.coefficients = None
+        super().__init__()
+
+    def fit(self, x_train, y_train):
+        self.coefficients = np.mean(y_train)
+
+    def predict(self, x_test):
+        return np.ones(x_test.shape[0]) * self.coefficients
+
+
+class SingleLinearRegression(RegressionModel):
+    def __init__(self, idx):
+        self.coefficients = None
+        self.idx = idx
+        super().__init__()
+
+    def fit(self, x_train, y_train):
+        self.coefficients = least_square_solution(
+            self.add_ones(x_train[:, self.idx]), y_train
+        )
+
+    def predict(self, x_test):
+        return self.add_ones(x_test[:, self.idx]) @ self.coefficients
+
+
+class MultipleLinearRegression(RegressionModel):
+    def __init__(self):
+        self.coefficients = None
+        super().__init__()
+        self.x_train = None
+
+    def fit(self, x_train, y_train):
+        self.coefficients = least_square_solution(self.add_ones(x_train), y_train)
+
+    def predict(self, x_test):
+        return self.add_ones(x_test) @ self.coefficients
+
+
+class GaussianKernelRidgeRegression(RegressionModel):
+    def __init__(self, gamma, sigma):
+        self.coefficients = None
+        self.gamma = gamma
+        self.sigma = sigma
+        self.x_train = None
+        super().__init__()
+
+    @staticmethod
[…]

### 2022-11-06 src/solutions/q1.py

@@ -1,0 +1,55 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from src.models.helpers import least_square_solution, mean_squared_error, phi_polynomial
+
+
+def _fit(x, y, ks):
+    weights = {}
+    for k in ks:
+        weights[k] = least_square_solution(phi_polynomial(x, k), y)
+    return weights
+
+
+def a(x, y, ks, figure_title, figure_path):
+    weights = _fit(x, y, ks)
+    x_plot = np.linspace(1, 4, 100).reshape(-1, 1)
+    plt.figure()
+    for k in ks:
+        mse = np.round(
+            mean_squared_error(y, np.dot(phi_polynomial(x, k), weights[k])), 2
+        )
+        plt.scatter(x, y)
+        plt.plot(
+            x_plot, np.dot(phi_polynomial(x_plot, k), weights[k]), label=f"{k=}, {mse=}"
+        )
+    plt.xlabel("x")
+    plt.ylabel("y")
+    plt.title(figure_title)
+    plt.legend()
+    plt.savefig(figure_path)
+
+
+def b(x, y, ks, table_path):
+    weights = _fit(x, y, ks)
+    w = np.zeros((len(ks), np.max(ks)))
+    for i, k in enumerate(ks):
+        w[i, :k] = weights[k].reshape(-1)
+    df = pd.DataFrame(w.T, columns=[f"{k=}" for k in ks])
+    df.index = ["1"] + [f"x^{i}" for i in range(1, np.max(ks))]
+    df.index.name = "Basis"
+    df.to_csv(table_path)
+
+
+def c(x, y, ks, table_path):
+    weights = _fit(x, y, ks)
+    mse = np.zeros((len(weights), 1))
+    for i, k in enumerate(ks):
+        mse[i] = np.round(
+            mean_squared_error(y, np.dot(phi_polynomial(x, k), weights[k])), 2
+        )
+    df = pd.DataFrame(mse.T, columns=[f"{k=}" for k in ks])
+    df.index = ["MSE"]
+    df.index.name = "Metric"
+    df.to_csv(table_path)

### 2022-11-06 src/solutions/q2_and_3.py

@@ -1,0 +1,132 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.constants import DEFAULT_SEED
+from src.models.helpers import least_square_solution, mean_squared_error, phi_polynomial
+
+
+def _g(x: np.ndarray) -> np.ndarray:
+    return np.sin(2 * np.pi * x) ** 2
+
+
+def _g_sigma(x: np.ndarray, sigma: float) -> np.ndarray:
+    e = np.random.normal(0, sigma, size=x.shape)
+    return _g(x) + e
+
+
+def _g_noisy_samples(number_of_sample_points, sigma, seed=DEFAULT_SEED):
+    np.random.seed(seed)
+    x_samples = np.random.uniform(low=0, high=1, size=(number_of_sample_points, 1))
+    y_samples_noisy = _g_sigma(x_samples, sigma).reshape(-1, 1)
+    return x_samples, y_samples_noisy
+
+
+def _calculate_mse(
+    number_of_sample_points, sigma, number_test_points, number_of_trials, phi, bases
+):
+    test_mse = np.zeros((number_of_trials, len(bases)))
+
+    np.random.seed(DEFAULT_SEED)
+    seeds = np.random.randint(low=number_of_trials, size=(number_of_trials,))
+    for i in range(number_of_trials):
+        x_samples, y_samples_noisy = _g_noisy_samples(
+            number_of_sample_points, sigma, seed=seeds[i]
+        )
+        weights_dict = {}
+        for base in bases:
+            weights_dict[base] = least_square_solution(
+                phi(x_samples, base), y_samples_noisy
+            )
+        for j, base in enumerate(weights_dict.keys()):
+            x_test = np.random.uniform(low=0, high=1, size=(number_test_points, 1))
+            y_test_actual = _g(x_test)
+            y_test_prediction = np.dot(phi(x_test, base), weights_dict[base])
+            test_mse[i, j] = mean_squared_error(y_test_actual, y_test_prediction)
+    return test_mse
+
+
+def a_i(number_of_sample_points, sigma, figure_title, figure_path):
+    x_samples, y_samples_noisy = _g_noisy_samples(number_of_sample_points, sigma)
+    x_plot = np.linspace(0, 1, 100).reshape(-1, 1)
+    y_plot = _g(x_plot)
+
+    plt.figure()
+    plt.plot(x_plot, y_plot)
[…]

### 2022-11-06 src/solutions/q4.py

@@ -1,0 +1,39 @@
+from typing import List
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.models.helpers import mean_squared_error, train_test_split
+from src.models.regression_models import (
+    MultipleLinearRegression,
+    NaiveLinearRegression,
+    RegressionModel,
+    SingleLinearRegression,
+)
+
+
+def _regression_report(models, x, y, iters):
+    mse_results = np.zeros((iters, len(models)))
+    for i in range(iters):
+        x_train, y_train, x_test, y_test = train_test_split(x, y, split=2 / 3)
+        for j, model in enumerate(models):
+            model.reset()
+            mse_results[i, j] = mean_squared_error(
+                model.fit_predict(x_train, y_train, x_test), y_test
+            )
+    return np.mean(mse_results, axis=0), np.std(mse_results, axis=0)
+
+
+def all_parts(x_train, y_train, data_columns, figure_title, figure_path):
+    models: List[RegressionModel] = []
+    models += [SingleLinearRegression(idx) for idx in range(12)]
+    models += [NaiveLinearRegression(), MultipleLinearRegression()]
+
+    mses, stds = _regression_report(models, x_train, y_train, iters=20)
+
+    axis_labels = data_columns[:12] + ["Naive", "MLR"]
+    plt.figure(figsize=(15, 3))
+    plt.bar(axis_labels, mses)
+    plt.ylabel("MSE")
+    plt.title(figure_title)
+    plt.savefig(figure_path)

### 2022-11-06 src/solutions/q5.py

@@ -1,0 +1,76 @@
+import numpy as np
+from jax import vmap
+
+from src.models.helpers import mean_squared_error, train_test_split
+from src.models.regression_models import GaussianKernelRidgeRegression
+
+
+def _make_folds(x, k):
+    indices = list(range(x.shape[0]))
+    np.random.shuffle(indices)
+    splits = np.array_split(indices, k)
+    return splits
+
+
+def _evaluate_mse_gkrr(gamma, sigma, x_train, y_train, x_test, y_test):
+    model = GaussianKernelRidgeRegression(gamma, sigma)
+    predictions = model.fit_predict(x_train=x_train, y_train=y_train, x_test=x_test)
+    return mean_squared_error(predictions, y_test)
+
+
+def _gkrr_model_selection(x, y, gammas, sigmas, k):
+    mses = np.zeros((len(sigmas), len(gammas), k))
+    folds = _make_folds(x, k)
+    for idx, split in enumerate(folds):
+        x_tr, y_tr, x_val, y_val = x[~split, :], y[~split], x[split, :], y[split]
+        mses[:, :, idx] = vmap(
+            lambda x_: vmap(
+                lambda y_: _evaluate_mse_gkrr(y_, x_, x_tr, y_tr, x_val, y_val)
+            )(gammas)
+        )(sigmas)
+    mses = np.mean(mses, axis=2)
+    best_sigma_idx, best_gamma_idx = np.unravel_index(mses.argmin(), mses.shape)
+    gamma = gammas[best_gamma_idx]
+    sigma = sigmas[best_sigma_idx]
+    return gamma, sigma, mses
+
+
+def _regression_report_with_gkrr(models, x, y, gammas, sigmas, iters):
+    train_errors = np.zeros((iters, len(models) + 1))
+    test_errors = train_errors.copy()
+    for i in range(iters):
+        x_train, y_train, x_test, y_test = train_test_split(x, y, split=2 / 3)
+        for j, model in enumerate(models):
+            model.reset()
+            model.fit(x_train, y_train)
+            train_errors[i, j] = mean_squared_error(model.predict(x_train), y_train)
+            test_errors[i, j] = mean_squared_error(model.predict(x_test), y_test)
+        gamma, sigma, _ = _gkrr_model_selection(
+            x=x_train, y=y_train, gammas=gammas, sigmas=sigmas, k=5
+        )
+        model = GaussianKernelRidgeRegression(gamma, sigma)
[…]

### 2022-11-06 src/solutions/q6.py

@@ -1,0 +1,29 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.models.knn import get_p_h, knn_prediction
+
+
+def all_parts(number_of_points, v, n_dims, figure_title, figure_path):
+    p_h = get_p_h(number_of_points, n_dims)
+    num_points_along_axis = 301
+    grid_axis = np.linspace(0, 1, num_points_along_axis)
+    x1, x2 = np.meshgrid(grid_axis, grid_axis)
+    test_points = np.stack((x1, x2)).reshape(2, -1).T
+    test_predictions = knn_prediction(p_h, test_points, k=v).reshape(
+        num_points_along_axis, num_points_along_axis
+    )
+
+    fig, ax = plt.subplots(1, 1)
+    fig.set_figwidth(10)
+    fig.set_figheight(10)
+
+    plt.imshow(np.flip(test_predictions, axis=0), extent=[0, 1, 0, 1])
+    x, y = p_h
+    idx_pos = np.where(y == 1)
+    idx_neg = np.where(y == 0)
+
+    plt.scatter(x[idx_pos, 0], x[idx_pos, 1], color="blue")
+    plt.scatter(x[idx_neg, 0], x[idx_neg, 1], color="green")
+    plt.title(figure_title)
+    plt.savefig(figure_path)

### 2022-11-06 src/solutions/q7.py

@@ -1,0 +1,64 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.constants import DEFAULT_SEED
+from src.models.knn import run_experiment
+
+
+def _protocol_a(
+    k_values,
+    v,
+    n_dims,
+    number_of_runs,
+    number_of_real_points,
+    number_of_train_points,
+    number_of_test_points,
+):
+    performance = np.zeros((len(k_values), number_of_runs))
+    np.random.seed(DEFAULT_SEED)
+    seeds = np.random.randint(
+        low=len(k_values) * number_of_runs, size=(len(k_values), number_of_runs)
+    )
+    for i, k_value in enumerate(k_values):
+        for j in range(number_of_runs):
+            performance[i, j] = run_experiment(
+                k_value,
+                v,
+                n_dims,
+                number_of_real_points,
+                number_of_train_points,
+                number_of_test_points,
+                seed=seeds[i, j],
+            )
+    return performance
+
+
+def all_parts(
+    k_values,
+    v,
+    n_dims,
+    number_of_runs,
+    number_of_real_points,
+    number_of_train_points,
+    number_of_test_points,
+    figure_title,
+    figure_path,
+):
+    performance = _protocol_a(
+        k_values,
+        v,
+        n_dims,
+        number_of_runs,
+        number_of_real_points,
+        number_of_train_points,
+        number_of_test_points,
+    )
+    fig, ax = plt.subplots(1, 1)
+    fig.set_figwidth(15)
+    fig.set_figheight(5)
+    plt.plot(k_values, np.mean(performance, axis=1))
+    plt.title(figure_title)
+    plt.xticks(k_values)
+    plt.xlabel("k Value")
+    plt.ylabel("Mean Test Set Error")
+    plt.savefig(figure_path)

### 2022-11-06 src/solutions/q8.py

@@ -1,0 +1,72 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from src.constants import DEFAULT_SEED
+from src.models.knn import run_experiment
+
+
+def _protocol_b(
+    k_values,
+    v,
+    n_dims,
+    number_of_runs,
+    number_of_real_points,
+    number_of_train_points_vector,
+    number_of_test_points,
+):
+    error = np.zeros(
+        (len(number_of_train_points_vector), len(k_values), number_of_runs)
+    )
+    np.random.seed(DEFAULT_SEED)
+    seeds = np.random.randint(
+        low=len(number_of_train_points_vector) * len(k_values) * number_of_runs,
+        size=(len(number_of_train_points_vector), len(k_values), number_of_runs),
+    )
+    for i, number_of_train_points in enumerate(number_of_train_points_vector):
+        for j, k_value in enumerate(k_values):
+            for k in range(number_of_runs):
+                error[i, j, k] = run_experiment(
+                    k_value,
+                    v,
+                    n_dims,
+                    number_of_real_points,
+                    number_of_train_points,
+                    number_of_test_points,
+                    seed=seeds[i, j, k],
+                )
+    return error
+
+
+def all_parts(
+    k_values,
+    v,
+    n_dims,
+    number_of_runs,
+    number_of_real_points,
+    number_of_train_points_vector,
+    number_of_test_points,
+    figure_title,
+    figure_path,
+):
+    error = _protocol_b(
+        k_values,
+        v,
+        n_dims,
+        number_of_runs,
+        number_of_real_points,
+        number_of_train_points_vector,
+        number_of_test_points,
+    )
+    fig, ax = plt.subplots(1, 1)
+    fig.set_figwidth(10)
+    fig.set_figheight(10)
+    plt.plot(
+        number_of_train_points_vector,
+        np.mean(k_values[np.argmin(error, axis=1)], axis=1),
+    )
+    plt.title(figure_title)
+    plt.xlabel("Number of Training Points (m)")
+    plt.ylabel("Optimal k Value")
+    plt.xticks(number_of_train_points_vector)
+    plt.yticks(k_values)
+    plt.savefig(figure_path)

### 2022-11-06 main.tex
add plots to tex file and big fix for q1b table orientation

@@
 \usepackage[colorlinks=true]{hyperref}
+\usepackage{graphicx}
+\usepackage{csvsimple}
 
@@
 
+\title{\textbf{COMP0086 Summative Assignment}}
+\author{Alexei Pisacane and Jian Shu (James) Wu \\ }
+\date{Nov 16, 2022}
+
 \begin{document}
+    \maketitle
 \begin{enumerate}[leftmargin=\labelsep]
-\item[8.]
+\section{PART I}
+\subsection{Linear Regression}
+\item[1.]
+    \begin{enumerate}
+        \item Superimposing the four different curves corresponding to each fit over the four given data points:
+        \begin{figure}[h!]
+        \centering
+        \includegraphics[scale=0.5]{outputs/python/q1/q1a}
+        \caption{Data set $\{(1, 3), (2, 2), (3, 0), (4, 5)\}$ fitted with basis $\{1, x\}$ and basis $\{1, x, x^2, x^3\}$ }
+        \label{fig:1a}
+        \end{figure}
 
-\item[9.]
+        \item The weights for the equations:
+        \begin{center}
+        \begin{tabular}{c|c|c|c|c}%
+         \textbf{Basis}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
+        \csvreader[head to column names]{outputs/python/q1/q1b.csv}{}% use head of csv as column names
+        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
+        \end{tabular}
+        \end{center}
+
+        \item The mean squared error for each fitted curve:
+        \begin{center}
+        \begin{tabular}{c|c|c|c|c}%
+         \textbf{Metric}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
+        \csvreader[head to column names]{outputs/python/q1/q1c.csv}{}% use head of csv as column names
+        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
+        \end{tabular}
+        \end{center}
+    \end{enumerate}
+\newpage
+\item[2.]
     \begin{enumerate}
         \item
-        let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
+        \begin{enumerate}
+            \item Superimposing the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the points of the above data set superimposed
+                    \begin{figure}[h]
+                    \centering
+                    \includegraphics[scale=0.5]{outputs/python/q2/q2ai}
+                    \caption{Noisy samples}
+                    \label{fig:2ai}
+                    \end{figure}
+            \item Fitting the data set with a polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves superimposed over a plot of data points:
+                    \begin{figure}[h]
+                    \centering
+                    \includegraphics[scale=0.5]{outputs/python/q2/q2aii}
+                    \caption{Polynomial fit curves}
+                    \label{fig:2aii}
+                    \end{figure}
+        \end{enumerate}
+\newpage
+        \item Plotting  the natural $\log$ ($\ln$) of the training error versus the polynomial dimension $k = 1, . . . , 18$:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q2/q2b}
+            \caption{Training Error of Polynomial Curves}
+            \label{fig:2b}
+            \end{figure}
+
+        \item Plotting the $\ln$ of the test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q2/q2c}
+            \caption{Testing Error of Polynomial Curves (1 trial)}
+            \label{fig:2c}
+            \end{figure}
+\newpage
+        \item Plotting the $\ln$ of the test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q2/q2d}
+            \caption{Testing Error of Polynomial Curves (100 trials)}
+            \label{fig:2d}
+            \end{figure}
+    \end{enumerate}
+\newpage
+\item[3.] Repeating 2 (b-d) with $\sin$ basis functions:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q3/q3b}
+            \caption{Training Error of $\sin$ Curves}
+            \label{fig:3b}
+            \end{figure}
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q3/q3c}
+            \caption{Testing Error of $\sin$ Curves (1 trial)}
+            \label{fig:3c}
+            \end{figure}
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q3/q3d}
+            \caption{Testing Error of $\sin$ Curves (100 trials)}
+            \label{fig:3d}
+            \end{figure}
+\newpage
+\subsection{Filtered Boston housing and kernels}
+\item[4.]
+\newpage
+\subsection{Kernelised ridge regression}
+\item[5.]
+\newpage
+\section{PART II}
+\subsection{$k$-Nearest Neighbors}
+\item[6.]Generating a random $h$:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q6/q6}
+            \caption{A hypothesis $h_{S,v}$ visualised with $|S|=100$ and $v=3$}
+            \label{fig:6a}
+            \end{figure}
+\newpage
+\item[7.]
+    \begin{enumerate}
+        \item Producing a visualisation using Protocol A:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q7/q7}
+            \caption{Protocol A}
+            \label{fig:7}
+            \end{figure}
+        \item TODO
+    \end{enumerate}
+\newpage
+\item[8.]
+    \begin{enumerate}
+        \item Producing a visualisation using Protocol B:
+            \begin{figure}[h]
+            \centering
+            \includegraphics[scale=0.5]{outputs/python/q8/q8}
+            \caption{Protocol B}
+            \label{fig:8}
+            \end{figure}
+        \item TODO
+    \end{enumerate}
+\newpage
+\section{PART III}
+\subsection{Questions}
+\item[9.] \begin{enumerate}
+              \item let $K_{c}(\textbf{x},\textbf{z}) = c+ \sum_{i=1}^{n}x_{i}z_{i} = c + \textbf{x}^{T}\textbf{z}$\\
         Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
@@
         \square$
-    \item
-    Using this kernel in our ridge regression, we arrive at the following prediction function:
+              \item Using this kernel in our ridge regression, we arrive at the following prediction function:
     \\
@@
     the constant function $f(x) = lc$
-    \\
+\end{enumerate}
+
 \newpage
-
-    \item
-    Define $g(t) := $sgn$(f(t)) = \frac{f(t)}{| f(t)|}$\\
+\item[10.]  Define $g(t) := $sgn$(f(t)) = \frac{f(t)}{| f(t)|}$\\
     \textbf{Proposition:}\\
@@
     \square$
-    \item
-    Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen.
+\newpage
+\item[11.] Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen.
 We first index all permissible moves by $T_{i,j}$, which has the effect of flipping the state of squares $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, as long as each coordinate is still on the grid.\\
@@
 \end{enumerate}
-\item
-
-\end{enumerate}
 \end{document}

### 2022-11-06 src/solutions/q1.py

@@ -36,7 +36,7 @@ def b(x, y, ks, table_path):
     w = np.zeros((len(ks), np.max(ks)))
     for i, k in enumerate(ks):
         w[i, :k] = weights[k].reshape(-1)
-    df = pd.DataFrame(w.T, columns=[f"{k=}" for k in ks])
+    df = pd.DataFrame(np.round(np.flip(w.T, axis=0), 2), columns=[f"{k=}" for k in ks])
     df.index = ["1"] + [f"x^{i}" for i in range(1, np.max(ks))]
     df.index.name = "Basis"
     df.to_csv(table_path)

### 2022-11-06 main.tex
add comment on protocol and adjust q8 axes

@@
             \end{figure}
-        \item TODO
+        \item We know that the data generating process uses $v=3$, so we would have initially expected the smallest test error to be located at the matching k-value, $k=3$.
+        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=9$.
+        As the k-value increases beyond $k=9$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
+        For $k<9$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
+        By averaging over 100 runs, the plot is relatively smooth allowing us to make generalisations about the relationship between k-value and mean test set error.
     \end{enumerate}

### 2022-11-06 src/solutions/q8.py

@@ -66,7 +66,6 @@ def all_parts(
     )
     plt.title(figure_title)
     plt.xlabel("Number of Training Points (m)")
-    plt.ylabel("Optimal k Value")
+    plt.ylabel("Optimal k-Value")
     plt.xticks(number_of_train_points_vector)
-    plt.yticks(k_values)
     plt.savefig(figure_path)

### 2022-11-06 main.tex
grammar fixes

@@
         \begin{enumerate}
-            \item Superimposing the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the points of the above data set superimposed
+            \item Plotting the function $sin^2(2\pi x)$ in the range $0 \leq x \leq 1$ with the sampled points superimposed:
                     \begin{figure}[h]
@@
                     \end{figure}
-            \item Fitting the data set with a polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves superimposed over a plot of data points:
+            \item Fitting the data set with polynomial bases of dimension $k = 2, 5, 10, 14, 18$ and plotting each of these 5 curves with the sampled points superimposed:
                     \begin{figure}[h]

### 2022-11-07 main.tex
update q8 plot
add comments on protocol b plot

@@
 \title{\textbf{COMP0086 Summative Assignment}}
-\author{Alexei Pisacane and Jian Shu (James) Wu \\ }
+\author{Alexei Pisacane \& Jian Shu (James) Wu \\ }
 \date{Nov 16, 2022}
@@
             \end{figure}
-        \item TODO
+        \item k-nearest neighbours is a non-parametric model, so when queried with a test point for prediction, the number of training points within a given fixed radius of that test point increases as the number of training points increases.
+        If we consider this fixed radius `sufficiently close' to make an informed prediction, the number of points within this radius will increase with more training points.
+        So as the number of training points increases, the optimal k would increase to include more of the training points within this same fixed radius.
+        We can see in the plot above that we see this general trend as expected, however there is considerable noise in the trend and so a smoother plot would likely requires more runs.
     \end{enumerate}

### 2022-11-08 main.tex
fix bug with using same seed for random initialisation

@@
         \item We know that the data generating process uses $v=3$, so we would have initially expected the smallest test error to be located at the matching k-value, $k=3$.
-        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=9$.
-        As the k-value increases beyond $k=9$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
-        For $k<9$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
+        However, the data generating process for the training data set labels \textit{and} the testing data set labels were injected with noise, so k-values greater than 3 have a ``de-noising'' effect allowing for better performance at around $k=7$.
+        As the k-value increases beyond $k=7$, this smoothing effect is too strong, causing the gradual increase in test error as the k value increases.
+        For $k<7$ and in particular $k<v=3$ we see the error growing because the model has small $k$ and is able to fit to the noise injected into the data generating process, corrupting the model.
         By averaging over 100 runs, the plot is relatively smooth allowing us to make generalisations about the relationship between k-value and mean test set error.

### 2022-11-08 main.py

@@ -162,19 +162,19 @@ if __name__ == "__main__":
         os.makedirs(Q7_OUTPUT_FOLDER)
     v = 3
     n_dims = 2
-    # # actual params
-    # k_values = np.arange(1, 50)
-    # number_of_runs = 100
-    # number_of_real_points = 100
-    # number_of_train_points = 4000
-    # number_of_test_points = 1000
-
-    # testing params
+    # actual params
     k_values = np.arange(1, 50)
-    number_of_runs = 3
-    number_of_real_points = 10
-    number_of_train_points = 40
-    number_of_test_points = 10
+    number_of_runs = 100
+    number_of_real_points = 100
+    number_of_train_points = 4000
+    number_of_test_points = 1000
+
+    # # testing params
+    # k_values = np.arange(1, 50)
+    # number_of_runs = 3
+    # number_of_real_points = 10
+    # number_of_train_points = 40
+    # number_of_test_points = 10
 
     q7.all_parts(
         k_values,
@@ -194,19 +194,19 @@ if __name__ == "__main__":
         os.makedirs(Q8_OUTPUT_FOLDER)
     v = 3
     n_dims = 2
-    # # actual params
-    # k_values = np.arange(1, 50)
-    # number_of_runs = 100
-    # number_of_real_points = 100
-    # number_of_train_points_vector = np.concatenate((np.array([100]), np.arange(500, 4500, 500)))
-    # number_of_test_points = 1000
-
-    # test params
+    # actual params
     k_values = np.arange(1, 50)
-    number_of_runs = 3
-    number_of_real_points = 10
-    number_of_train_points_vector = np.arange(50, 110, 10)
-    number_of_test_points = 10
+    number_of_runs = 100
+    number_of_real_points = 100
+    number_of_train_points_vector = np.concatenate((np.array([100]), np.arange(500, 4500, 500)))
+    number_of_test_points = 1000
+
+    # # test params
+    # k_values = np.arange(1, 50)
+    # number_of_runs = 3
+    # number_of_real_points = 10
+    # number_of_train_points_vector = np.arange(50, 110, 10)
+    # number_of_test_points = 10
 
     q8.all_parts(
         k_values,

### 2022-11-08 src/models/knn.py

@@ -2,16 +2,12 @@ from typing import Tuple
 
 import numpy as np
 
-from src.constants import DEFAULT_SEED
-
-
 def get_p_h(
-    number_of_points: int, n_dims: int, seed: int = DEFAULT_SEED
+    number_of_points: int, n_dims: int
 ) -> Tuple[np.ndarray, np.ndarray]:
     """
     generate data for a voted-center hypothesis
     """
-    np.random.seed(seed)
     x = np.random.uniform(low=0, high=1, size=(number_of_points, n_dims))
     y = np.random.choice(a=[0, 1], size=number_of_points)
     return x, y
@@ -86,7 +82,6 @@ def generate_noisy_data(
     number_samples: int,
     v: int,
     n_dims: int,
-    seed: int = DEFAULT_SEED,
 ) -> Tuple[np.ndarray, np.ndarray]:
     """
     p_h: data for a voted-center hypothesis
@@ -96,7 +91,6 @@ def generate_noisy_data(
     return x and noisy labels
     """
     # generate x uniformly
-    np.random.seed(seed)
     x = np.random.uniform(low=0, high=1, size=(number_samples, n_dims))
     noisy_labels = _noisy_knn_prediction(train_data=p_h, test_points=x, k=v)
     return x, noisy_labels
@@ -109,9 +103,8 @@ def run_experiment(
     number_of_real_points,
     number_of_train_points,
     number_of_test_points,
-    seed,
 ):
-    p_h = get_p_h(number_of_real_points, n_dims, seed)
+    p_h = get_p_h(number_of_real_points, n_dims)
     data_train = generate_noisy_data(
         p_h, number_samples=number_of_train_points, v=v, n_dims=n_dims
     )

### 2022-11-08 src/solutions/q2_and_3.py

@@ -14,8 +14,7 @@ def _g_sigma(x: np.ndarray, sigma: float) -> np.ndarray:
     return _g(x) + e
 
 
-def _g_noisy_samples(number_of_sample_points, sigma, seed=DEFAULT_SEED):
-    np.random.seed(seed)
+def _g_noisy_samples(number_of_sample_points, sigma):
     x_samples = np.random.uniform(low=0, high=1, size=(number_of_sample_points, 1))
     y_samples_noisy = _g_sigma(x_samples, sigma).reshape(-1, 1)
     return x_samples, y_samples_noisy
@@ -29,8 +28,9 @@ def _calculate_mse(
     np.random.seed(DEFAULT_SEED)
     seeds = np.random.randint(low=number_of_trials, size=(number_of_trials,))
     for i in range(number_of_trials):
+        np.random.seed(seeds[i])
         x_samples, y_samples_noisy = _g_noisy_samples(
-            number_of_sample_points, sigma, seed=seeds[i]
+            number_of_sample_points, sigma,
         )
         weights_dict = {}
         for base in bases:
@@ -79,6 +79,7 @@ def a_ii(
     plt.title(figure_title)
     plt.xlabel("x")
     plt.ylabel("y")
+    plt.ylim([-2.5, 2.5])
     plt.legend()
     plt.savefig(figure_path)
 

### 2022-11-08 src/solutions/q7.py

@@ -21,6 +21,7 @@ def _protocol_a(
     )
     for i, k_value in enumerate(k_values):
         for j in range(number_of_runs):
+            np.random.seed(seeds[i, j])
             performance[i, j] = run_experiment(
                 k_value,
                 v,
@@ -28,7 +29,6 @@ def _protocol_a(
                 number_of_real_points,
                 number_of_train_points,
                 number_of_test_points,
-                seed=seeds[i, j],
             )
     return performance
 

### 2022-11-08 src/solutions/q8.py

@@ -25,6 +25,7 @@ def _protocol_b(
     for i, number_of_train_points in enumerate(number_of_train_points_vector):
         for j, k_value in enumerate(k_values):
             for k in range(number_of_runs):
+                np.random.seed(seeds[i, j, k])
                 error[i, j, k] = run_experiment(
                     k_value,
                     v,
@@ -32,7 +33,6 @@ def _protocol_b(
                     number_of_real_points,
                     number_of_train_points,
                     number_of_test_points,
-                    seed=seeds[i, j, k],
                 )
     return error
 

### 2022-11-08 submission.tex
reorganise file structure

--- 2022-11-08 main.tex
@@
         \centering
-        \includegraphics[scale=0.5]{outputs/python/q1/q1a}
+        \includegraphics[scale=0.5]{outputs/q1/q1a}
         \caption{Data set $\{(1, 3), (2, 2), (3, 0), (4, 5)\}$ fitted with basis $\{1, x\}$ and basis $\{1, x, x^2, x^3\}$ }
@@
          \textbf{Basis}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
-        \csvreader[head to column names]{outputs/python/q1/q1b.csv}{}% use head of csv as column names
+        \csvreader[head to column names]{outputs/q1/q1b.csv}{}% use head of csv as column names
         {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
@@
          \textbf{Metric}&\textbf{k=1}&\textbf{k=2}&\textbf{k=3} &\textbf{k=4}% specify table head
-        \csvreader[head to column names]{outputs/python/q1/q1c.csv}{}% use head of csv as column names
+        \csvreader[head to column names]{outputs/q1/q1c.csv}{}% use head of csv as column names
         {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
@@
                     \centering
-                    \includegraphics[scale=0.5]{outputs/python/q2/q2ai}
+                    \includegraphics[scale=0.5]{outputs/q2/q2ai}
                     \caption{Noisy samples}
@@
                     \centering
-                    \includegraphics[scale=0.5]{outputs/python/q2/q2aii}
+                    \includegraphics[scale=0.5]{outputs/q2/q2aii}
                     \caption{Polynomial fit curves}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q2/q2b}
+            \includegraphics[scale=0.5]{outputs/q2/q2b}
             \caption{Training Error of Polynomial Curves}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q2/q2c}
+            \includegraphics[scale=0.5]{outputs/q2/q2c}
             \caption{Testing Error of Polynomial Curves (1 trial)}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q2/q2d}
+            \includegraphics[scale=0.5]{outputs/q2/q2d}
             \caption{Testing Error of Polynomial Curves (100 trials)}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q3/q3b}
+            \includegraphics[scale=0.5]{outputs/q3/q3b}
             \caption{Training Error of $\sin$ Curves}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q3/q3c}
+            \includegraphics[scale=0.5]{outputs/q3/q3c}
             \caption{Testing Error of $\sin$ Curves (1 trial)}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q3/q3d}
+            \includegraphics[scale=0.5]{outputs/q3/q3d}
             \caption{Testing Error of $\sin$ Curves (100 trials)}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q6/q6}
+            \includegraphics[scale=0.5]{outputs/q6/q6}
             \caption{A hypothesis $h_{S,v}$ visualised with $|S|=100$ and $v=3$}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q7/q7}
+            \includegraphics[scale=0.5]{outputs/q7/q7}
             \caption{Protocol A}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/python/q8/q8}
+            \includegraphics[scale=0.5]{outputs/q8/q8}
             \caption{Protocol B}

### 2022-11-08 src/constants.py

@@ -1,2 +1,2 @@
-OUTPUTS_FOLDER = "outputs/python"
+OUTPUTS_FOLDER = "outputs"
 DEFAULT_SEED = 0

### 2022-11-11 submission.tex
test overleaf
Updates from Overleaf
Main

@@
 \usepackage{csvsimple}
-
+\usepackage{luacode}
 \setlength{\droptitle}{-6em}
@@
 \title{\textbf{COMP0086 Summative Assignment}}
-\author{Alexei Pisacane \& Jian Shu (James) Wu \\ }
+\author{Alexei Pisacane and Jian Shu (James) Wu \\ }
 \date{Nov 16, 2022}
@@
     \item[4.]
+    \begin{enumerate}
+        \item 
+        We interpret the naive linear regression model using the existing framework for least squares regressors.\\
+        Namely, we have:\\
+        $w^* = (X^TX)^{-1}X^{T} y, X = (1,\dots,1)^{T} $\\
+        \[\implies w* = m^{-1}  \sum_{i} 1*y_{i} = \bar{y}\]\\
+        \[\implies f(x_{i}) = 1 \times w^{*} = \bar{y}\]\\
+        We split the data using our train test split function, and train naive, single and multiple linear regression models.
+            We repeat this 20 times and report the MSE on training and test sets.\\
+
+        Here are the plots of training and test error:\\
+        \includegraphics[scale=0.5]{outputs/q4/q4_train.png}\\
+        \includegraphics[scale=0.5]{outputs/q4/q4_test.png}\\
+    \end{enumerate}
 \newpage
@@
 \item[5.]
-\newpage
+We fit our kernel ridge regressors for each parameter pair over 5 cross validation folds,
+and search for the pair minimising our mean squared error.\\
+
+Here are the optimal parameters along with the minimal mean squared error:\\
+
+\item The mean squared error for each fitted curve:
+\begin{center}
+\begin{tabular}{c|c|c}%
+\textbf{Gamma}&\textbf{Sigma}&\textbf{MSE}% specify table head
+\csvreader[head to column names]{outputs/q5/optimal_gkrr_parameters.csv}{}% use head of csv as column names
+{\\\hline\csvcoli&\csvcolii&\csvcoliii}% specify your coloumns here
+\end{tabular}
+\end{center}
+
+\\
+Here is our contour plot for mse over our parameter grid:\\
+
+\includegraphics[scale = 0.5]{outputs/q5/contour_plot.png}\\
+
+\item[5.]
+
+Here is our final regression report over all oour models, run 20 times each.\\
+
+\item The mean squared error for each fitted curve:
+\begin{center}
+\begin{tabular}{c|c|c|c|c}%
+\textbd{model}&\textbf{train mse}&\textbf{train std}&\textbf{test mse}&\textbf{test std}% specify table head
+\csvreader[head to column names]{outputs/q5/regression_report.csv}{}% use head of csv as column names
+{\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
+\end{tabular}
+\end{center}
+
 \section{PART II}
@@
         Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
-        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R},
-         \{ \textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:
+        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R}, {\textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:
 
-        $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) \ge 0$
+        $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) \ge 0 $\\
         We expand our kernel function to give: \\
-
         \[\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) =  \sum_{n,m} cu_{n} u_{m} + \sum_{n,m} \langle\textbf{x}_{n}, \textbf{x}_{m}\rangle u_{n} u_{m}\]
@@
         \textbf{Proposition}
-
-        $K_{c}(\cdot, \cdot)$ is psd iff $c \ge0$
-
+        $K_{c}(\cdot, \cdot)$ is psd iff $c \ge0$ \\
         \textbf{Proof:}\\
@@
     We note that as c becomes large, $\alpha \to 0$ and hence the predictions for $\hat{y}_{test}$ approach
-    the constant function $f(x) = lc$
+    the constant function $f(x) = lc$\\
+
+    Hence, adding c to our kernel acts like a regulariser in the limit.\\ 
 \end{enumerate}
@@
 
-    $K = I_{l} + \tilde{K}$, where $\tilde{K}_{ij} = K(x_i, x_j)$, $i \ne j$. We note here that as $\beta \to \infty$, $ \tilde{K} \to 0$.\\
+    $K = I_{l} + \tilde{K}$, where $\tilde{K}_{ij} = K(x_i, x_j)$, $i \ne j$. We note here that as $\beta \to \infty$, $\tilde{K} \to 0$.\\
 
@@
     Let's assume that there exists a unique point x in our training set of minimal distance to our test point.\\
-
     Define $d_{i} := \|x_{test} - x_{i}\|^{2}$, and $d* := min_{i} d_{i}$\\
-    \\
     $g(t) = \frac{y_{*} exp(-\beta d_{*})}{|\sum_{i} y_{i} exp(-\beta d_{i})|} + \sum_{i\ne *}\frac{y_{i} exp(-\beta d_{i})}{|\sum_{i} y_{i} exp(-\beta 
@@
     Note for $d_{i} \ne d_{*}$, $exp(-\beta(d_{i} - d_{*})) \to 0$ as $\beta \to \infty$. Hence:\\
-    $g(t) \to \frac{y_{*}}{|y_{*} + 0|} + \frac{0}{|y_{*} + 0|} = y_{*} = y_{i} : x_{i} = min_{i} \|x_{test} - x_{i}\|$ which is the required 1-NN predictor.\\$
-    \square$
+    $g(t) \to \frac{y_{*}}{|y_{*} + 0|} + \frac{0}{|y_{*} + 0|} = y_{*} = y_{i} : x_{i} = min_{i} \|x_{test} - x_{i}\|$ which is the required 1-NN predictor.\\
+
 \newpage
-\item[11.] Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen.
+\item[11.] \\
+Given a whack-a-mole grid of size n, it is solvable if we can apply a sequence from our $n^{2}$ permissible moves that results in a blank screen.
 We first index all permissible moves by $T_{i,j}$, which has the effect of flipping the state of squares $(i,j),(i-1,j),(i+1,j),(i,j-1)(i,j+1)$, as long as each coordinate is still on the grid.\\

### 2022-11-11 main.py

@@ -2,12 +2,15 @@ import os
 
 import numpy as np
 import pandas as pd
+import jax
 
 from src.constants import OUTPUTS_FOLDER
 from src.models.helpers import phi_polynomial, phi_sin, train_test_split
-from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
+from src.solutions import q1, q2_and_3, q4_and_5, q6, q7, q8
 
 if __name__ == "__main__":
+    jax.config.update('jax_platform_name', 'cpu')
+
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
 
@@ -115,31 +118,35 @@ if __name__ == "__main__":
         phi=phi_sin,
     )
 
-    # Question 4
+    # Question 4 and 5
     Q4_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q4")
+    Q5_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q5")
+
     if not os.path.exists(Q4_OUTPUT_FOLDER):
         os.makedirs(Q4_OUTPUT_FOLDER)
+
+    
+    if not os.path.exists(Q5_OUTPUT_FOLDER):
+        os.makedirs(Q5_OUTPUT_FOLDER)
+
     data = pd.read_csv("data/Boston-filtered.csv")
     x = np.array(data)
     x, y = x[:, :-1], x[:, -1]
     x_train, y_train, x_test, y_test = train_test_split(x, y, 2 / 3)
-    q4.all_parts(
+
+    q4_and_5.all_parts(
         x_train,
         y_train,
-        data_columns=list(data.columns),
-        figure_title="Question 4: ",
-        figure_path=os.path.join(Q4_OUTPUT_FOLDER, "q4.png"),
-    )
+        data_columns=list(data.columns),  # type: ignore
+        figure_title_train="MSE Train",
+        figure_title_test="MSE Test",
+        figure_path_train=os.path.join(Q4_OUTPUT_FOLDER, "q4_train.png"),
+        figure_path_test =os.path.join(Q4_OUTPUT_FOLDER, "q4_test.png"),
+        gkrr_param_path = os.path.join(Q5_OUTPUT_FOLDER, 'optimal_gkrr_parameters.csv'),
+        contour_path = os.path.join(Q5_OUTPUT_FOLDER, 'contour_plot'),
[…]

### 2022-11-11 src/solutions/q4.py

@@ -1,39 +1,0 @@
-from typing import List
-
-import matplotlib.pyplot as plt
-import numpy as np
-
-from src.models.helpers import mean_squared_error, train_test_split
-from src.models.regression_models import (
-    MultipleLinearRegression,
-    NaiveLinearRegression,
-    RegressionModel,
-    SingleLinearRegression,
-)
-
-
-def _regression_report(models, x, y, iters):
-    mse_results = np.zeros((iters, len(models)))
-    for i in range(iters):
-        x_train, y_train, x_test, y_test = train_test_split(x, y, split=2 / 3)
-        for j, model in enumerate(models):
-            model.reset()
-            mse_results[i, j] = mean_squared_error(
-                model.fit_predict(x_train, y_train, x_test), y_test
-            )
-    return np.mean(mse_results, axis=0), np.std(mse_results, axis=0)
-
-
-def all_parts(x_train, y_train, data_columns, figure_title, figure_path):
-    models: List[RegressionModel] = []
-    models += [SingleLinearRegression(idx) for idx in range(12)]
-    models += [NaiveLinearRegression(), MultipleLinearRegression()]
-
-    mses, stds = _regression_report(models, x_train, y_train, iters=20)
-
-    axis_labels = data_columns[:12] + ["Naive", "MLR"]
-    plt.figure(figsize=(15, 3))
-    plt.bar(axis_labels, mses)
-    plt.ylabel("MSE")
-    plt.title(figure_title)
-    plt.savefig(figure_path)

### 2022-11-11 src/solutions/q5.py

@@ -1,76 +1,0 @@
-import numpy as np
-from jax import vmap
-
-from src.models.helpers import mean_squared_error, train_test_split
-from src.models.regression_models import GaussianKernelRidgeRegression
-
-
-def _make_folds(x, k):
-    indices = list(range(x.shape[0]))
-    np.random.shuffle(indices)
-    splits = np.array_split(indices, k)
-    return splits
-
-
-def _evaluate_mse_gkrr(gamma, sigma, x_train, y_train, x_test, y_test):
-    model = GaussianKernelRidgeRegression(gamma, sigma)
-    predictions = model.fit_predict(x_train=x_train, y_train=y_train, x_test=x_test)
-    return mean_squared_error(predictions, y_test)
-
-
-def _gkrr_model_selection(x, y, gammas, sigmas, k):
-    mses = np.zeros((len(sigmas), len(gammas), k))
-    folds = _make_folds(x, k)
-    for idx, split in enumerate(folds):
-        x_tr, y_tr, x_val, y_val = x[~split, :], y[~split], x[split, :], y[split]
-        mses[:, :, idx] = vmap(
-            lambda x_: vmap(
-                lambda y_: _evaluate_mse_gkrr(y_, x_, x_tr, y_tr, x_val, y_val)
-            )(gammas)
-        )(sigmas)
-    mses = np.mean(mses, axis=2)
-    best_sigma_idx, best_gamma_idx = np.unravel_index(mses.argmin(), mses.shape)
-    gamma = gammas[best_gamma_idx]
-    sigma = sigmas[best_sigma_idx]
-    return gamma, sigma, mses
-
-
-def _regression_report_with_gkrr(models, x, y, gammas, sigmas, iters):
-    train_errors = np.zeros((iters, len(models) + 1))
-    test_errors = train_errors.copy()
-    for i in range(iters):
-        x_train, y_train, x_test, y_test = train_test_split(x, y, split=2 / 3)
-        for j, model in enumerate(models):
-            model.reset()
-            model.fit(x_train, y_train)
-            train_errors[i, j] = mean_squared_error(model.predict(x_train), y_train)
-            test_errors[i, j] = mean_squared_error(model.predict(x_test), y_test)
-        gamma, sigma, _ = _gkrr_model_selection(
-            x=x_train, y=y_train, gammas=gammas, sigmas=sigmas, k=5
-        )
-        model = GaussianKernelRidgeRegression(gamma, sigma)
[…]

### 2022-11-11 src/solutions/q4_and_5.py
Main

@@ -1,0 +1,150 @@
+from typing import List
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from jax import vmap
+
+from mpl_toolkits import mplot3d
+
+from src.models.helpers import mean_squared_error, train_test_split
+from src.models.regression_models import (
+    MultipleLinearRegression,
+    NaiveLinearRegression,
+    RegressionModel,
+    SingleLinearRegression,
+    GaussianKernelRidgeRegression
+)
+
+def _regression_report(models, x, y, iters):
+    mse_results_test = np.zeros((iters, len(models)))
+    mse_results_train = np.zeros((iters, len(models)))
+
+    for i in range(iters):
+        x_train, y_train, x_test, y_test = train_test_split(x, y, split=2 / 3)
+        for j, model in enumerate(models):
+            model.reset()
+            mse_results_test[i, j] = mean_squared_error(
+                model.fit_predict(x_train, y_train, x_test), y_test
+            )
+            
+            mse_results_train[i, j] = mean_squared_error(
+                model.predict(x_train), y_train
+            )
+    return np.mean(mse_results_test, axis=0), np.std(mse_results_test, axis=0), np.mean(mse_results_train, axis=0), np.std(mse_results_train, axis=0)
+
+
+def _make_folds(x, k):
+    indices = list(range(x.shape[0]))
+    np.random.shuffle(indices)
+    splits = np.array_split(indices, k)
+    return splits
+
+
+def _evaluate_mse_gkrr(gamma, sigma, x_train, y_train, x_test, y_test):
+    model = GaussianKernelRidgeRegression(gamma, sigma)
+    predictions = model.fit_predict(x_train=x_train, y_train=y_train, x_test=x_test)
+    return mean_squared_error(predictions, y_test)
+
+
+def _gkrr_model_selection(x, y, gammas, sigmas, k):
+    mses = np.zeros((len(sigmas), len(gammas), k))
+    folds = _make_folds(x, k)
+    for idx, split in enumerate(folds):
+        x_tr, y_tr, x_val, y_val = x[~split, :], y[~split], x[split, :], y[split]
+        mses[:, :, idx] = vmap(
+            lambda x_: vmap(
+                lambda y_: _evaluate_mse_gkrr(y_, x_, x_tr, y_tr, x_val, y_val)
[…]

### 2022-11-11 main.py
format with black

@@ -1,15 +1,15 @@
 import os
 
+import jax
 import numpy as np
 import pandas as pd
-import jax
 
 from src.constants import OUTPUTS_FOLDER
 from src.models.helpers import phi_polynomial, phi_sin, train_test_split
 from src.solutions import q1, q2_and_3, q4_and_5, q6, q7, q8
 
 if __name__ == "__main__":
-    jax.config.update('jax_platform_name', 'cpu')
+    jax.config.update("jax_platform_name", "cpu")
 
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
@@ -125,7 +125,6 @@ if __name__ == "__main__":
     if not os.path.exists(Q4_OUTPUT_FOLDER):
         os.makedirs(Q4_OUTPUT_FOLDER)
 
-    
     if not os.path.exists(Q5_OUTPUT_FOLDER):
         os.makedirs(Q5_OUTPUT_FOLDER)
 
@@ -141,12 +140,11 @@ if __name__ == "__main__":
         figure_title_train="MSE Train",
         figure_title_test="MSE Test",
         figure_path_train=os.path.join(Q4_OUTPUT_FOLDER, "q4_train.png"),
-        figure_path_test =os.path.join(Q4_OUTPUT_FOLDER, "q4_test.png"),
-        gkrr_param_path = os.path.join(Q5_OUTPUT_FOLDER, 'optimal_gkrr_parameters.csv'),
-        contour_path = os.path.join(Q5_OUTPUT_FOLDER, 'contour_plot'),
-        report_path= os.path.join(Q5_OUTPUT_FOLDER, 'regression_report.csv')
+        figure_path_test=os.path.join(Q4_OUTPUT_FOLDER, "q4_test.png"),
+        gkrr_param_path=os.path.join(Q5_OUTPUT_FOLDER, "optimal_gkrr_parameters.csv"),
+        contour_path=os.path.join(Q5_OUTPUT_FOLDER, "contour_plot"),
+        report_path=os.path.join(Q5_OUTPUT_FOLDER, "regression_report.csv"),
     )  # type: ignore
-
 
     # Question 6
     Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")

### 2022-11-11 src/models/knn.py

@@ -2,9 +2,8 @@ from typing import Tuple
 
 import numpy as np
 
-def get_p_h(
-    number_of_points: int, n_dims: int
-) -> Tuple[np.ndarray, np.ndarray]:
+
+def get_p_h(number_of_points: int, n_dims: int) -> Tuple[np.ndarray, np.ndarray]:
     """
     generate data for a voted-center hypothesis
     """

### 2022-11-11 src/solutions/q2_and_3.py

@@ -30,7 +30,8 @@ def _calculate_mse(
     for i in range(number_of_trials):
         np.random.seed(seeds[i])
         x_samples, y_samples_noisy = _g_noisy_samples(
-            number_of_sample_points, sigma,
+            number_of_sample_points,
+            sigma,
         )
         weights_dict = {}
         for base in bases:

### 2022-11-11 src/solutions/q4_and_5.py

@@ -4,17 +4,17 @@ import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 from jax import vmap
-
 from mpl_toolkits import mplot3d
 
 from src.models.helpers import mean_squared_error, train_test_split
 from src.models.regression_models import (
+    GaussianKernelRidgeRegression,
     MultipleLinearRegression,
     NaiveLinearRegression,
     RegressionModel,
     SingleLinearRegression,
-    GaussianKernelRidgeRegression
 )
+
 
 def _regression_report(models, x, y, iters):
     mse_results_test = np.zeros((iters, len(models)))
@@ -27,11 +27,16 @@ def _regression_report(models, x, y, iters):
             mse_results_test[i, j] = mean_squared_error(
                 model.fit_predict(x_train, y_train, x_test), y_test
             )
-            
+
             mse_results_train[i, j] = mean_squared_error(
                 model.predict(x_train), y_train
             )
-    return np.mean(mse_results_test, axis=0), np.std(mse_results_test, axis=0), np.mean(mse_results_train, axis=0), np.std(mse_results_train, axis=0)
+    return (
+        np.mean(mse_results_test, axis=0),
+        np.std(mse_results_test, axis=0),
+        np.mean(mse_results_train, axis=0),
+        np.std(mse_results_train, axis=0),
+    )
 
 
 def _make_folds(x, k):
@@ -64,7 +69,9 @@ def _gkrr_model_selection(x, y, gammas, sigmas, k):
     return gamma, sigma, mses
 
 
-def _regression_report_with_gkrr(models : List[RegressionModel], x, y, gammas, sigmas, iters):
+def _regression_report_with_gkrr(
+    models: List[RegressionModel], x, y, gammas, sigmas, iters
+):
     train_errors = np.zeros((iters, len(models) + 1))
     test_errors = train_errors.copy()
     for i in range(iters):
@@ -99,15 +106,18 @@ def all_parts(
     figure_path_test,
     gkrr_param_path,
     contour_path,
-    report_path):
-    
+    report_path,
+):
+
     x_train, y_train, x_test, y_test = train_test_split(x, y, 2 / 3)
 
     models: List[RegressionModel] = []
     models += [SingleLinearRegression(idx) for idx in range(12)]
[…]

### 2022-11-14 src/solutions/q4_and_5.py
14-11

@@ -5,7 +5,6 @@ import numpy as np
 import pandas as pd
 from jax import vmap
 
-from mpl_toolkits import mplot3d
 
 from src.models.helpers import mean_squared_error, train_test_split
 from src.models.regression_models import (
@@ -15,6 +14,9 @@ from src.models.regression_models import (
     SingleLinearRegression,
     GaussianKernelRidgeRegression
 )
+
+import plotly.graph_objects as go
+
 
 def _regression_report(models, x, y, iters):
     mse_results_test = np.zeros((iters, len(models)))
@@ -129,12 +131,14 @@ def all_parts(
     gamma,sigma, mses = _gkrr_model_selection(x = x_train,y = y_train, gammas = gammas, sigmas = sigmas, k = 5)   # type: ignore
     GKRR_params = pd.DataFrame({'Optimal Gamma: ' : gamma, 'Optimal Sigma: ' : sigma, 'mse: ' : mses.min()}, index = [0])
     GKRR_params.to_csv(gkrr_param_path, index = False)
-    fig = plt.figure()
-    ax = plt.axes(projection='3d')
-    ax.contour3D(gammas, sigmas, mses)  # type: ignore
-    ax.set_xlabel('gamma')
-    ax.set_ylabel('sigma')
-    ax.set_zlabel('mse')  # type: ignore
+    surface = go.Surface(x = np.log(gammas), y = np.log(sigmas), z=np.log(mses))
+    camera = dict(
+        up=dict(x=0, y=0, z=1),
+        center=dict(x=0, y=0, z=0),
+        eye=dict(x=1.25, y=1.25, z=1)
+    )
+    fig = go.Figure(data=surface)
+    fig.update_layout(scene_camera=camera)
     plt.savefig(contour_path)
 
     axis_labels += ['GKRR']

### 2022-11-14 main.py
plotly

@@ -142,7 +142,7 @@ if __name__ == "__main__":
         figure_path_train=os.path.join(Q4_OUTPUT_FOLDER, "q4_train.png"),
         figure_path_test=os.path.join(Q4_OUTPUT_FOLDER, "q4_test.png"),
         gkrr_param_path=os.path.join(Q5_OUTPUT_FOLDER, "optimal_gkrr_parameters.csv"),
-        contour_path=os.path.join(Q5_OUTPUT_FOLDER, "contour_plot"),
+        contour_path=os.path.join(Q5_OUTPUT_FOLDER, "contour_plot.png"),
         report_path=os.path.join(Q5_OUTPUT_FOLDER, "regression_report.csv"),
     )  # type: ignore
 

### 2022-11-14 src/solutions/q4_and_5.py

@@ -4,7 +4,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 from jax import vmap
-from mpl_toolkits import mplot3d
+import plotly.graph_objects as go
+import plotly.io as pio
 
 from src.models.helpers import mean_squared_error, train_test_split
 from src.models.regression_models import (
@@ -142,13 +143,26 @@ def all_parts(
         index=[0],
     )
     GKRR_params.to_csv(gkrr_param_path, index=False)
-    fig = plt.figure()
-    ax = plt.axes(projection="3d")
-    ax.contour3D(gammas, sigmas, mses)  # type: ignore
-    ax.set_xlabel("gamma")
-    ax.set_ylabel("sigma")
-    ax.set_zlabel("mse")  # type: ignore
-    plt.savefig(contour_path)
+
+
+    surface = go.Surface(x = np.log(gammas), y = np.log(sigmas), z=np.log(mses))
+    camera = dict(
+        up=dict(x=0, y=0, z=1),
+        center=dict(x=0, y=0, z=0),
+        eye=dict(x=1.25, y=1.25, z=1)
+    )
+    fig = go.Figure(data=surface)
+    fig.update_layout(scene_camera=camera)
+    pio.write_image(fig, contour_path, format='png')
+
+
+ #   fig = plt.figure()
+  #  ax = plt.axes(projection="3d")
+   # ax.contour3D(gammas, sigmas, mses)  # type: ignore
+   # ax.set_xlabel("gamma")
+   ## ax.set_ylabel("sigma")
+   # ax.set_zlabel("mse")  # type: ignore
+   # plt.savefig(contour_path)
 
     axis_labels += ["GKRR"]
     train_mse, train_std, test_mse, test_std = _regression_report_with_gkrr(

### 2022-11-14 src/solutions/q4_and_5.py
bug fix for gkrr

@@ -46,27 +46,50 @@ def _make_folds(x, k):
     return splits
 
 
-def _evaluate_mse_gkrr(gamma, sigma, x_train, y_train, x_test, y_test):
+def _evaluate_mse_gkrr(gamma: float, sigma: float, x_train: np.ndarray, y_train: np.ndarray, x_test: np.ndarray, y_test: np.ndarray):
+    """
+
+    :param gamma: gamma value
+    :param sigma: sigma value
+    :param x_train: (N_train, D)
+    :param y_train: (N_train, )
+    :param x_test: (N_test, D)
+    :param y_test:(N_test, )
+    :return:
+    """
     model = GaussianKernelRidgeRegression(gamma, sigma)
     predictions = model.fit_predict(x_train=x_train, y_train=y_train, x_test=x_test)
     return mean_squared_error(predictions, y_test)
 
 
-def _gkrr_model_selection(x, y, gammas, sigmas, k):
-    mses = np.zeros((len(sigmas), len(gammas), k))
-    folds = _make_folds(x, k)
+def _gkrr_model_selection(
+        x: np.ndarray,
+        y: np.ndarray,
+        gammas: np.ndarray,
+        sigmas: np.ndarray,
+        k: int
+):
+    """
+
+    :param x: (N, D)
+    :param y: (N, )
+    :param gammas: (G, )
+    :param sigmas: (S, )
+    :param k: int
+    :return:
+    """
+    mses = np.zeros((len(sigmas), len(gammas), k)) # (S, G, k)
+    folds: List[np.ndarray] = _make_folds(x, k)
     for idx, split in enumerate(folds):
-        x_tr, y_tr, x_val, y_val = x[~split, :], y[~split], x[split, :], y[split]
+        x_tr, y_tr, x_val, y_val = np.delete(x, split, axis=0), np.delete(y, split, axis=0), x[split, :], y[split]
         mses[:, :, idx] = vmap(
-            lambda x_: vmap(
-                lambda y_: _evaluate_mse_gkrr(y_, x_, x_tr, y_tr, x_val, y_val)
+            lambda sigma_i: vmap(
+                lambda gamma_j: _evaluate_mse_gkrr(gamma_j, sigma_i, x_tr, y_tr, x_val, y_val)
             )(gammas)
         )(sigmas)
     mses = np.mean(mses, axis=2)
     best_sigma_idx, best_gamma_idx = np.unravel_index(mses.argmin(), mses.shape)
-    gamma = gammas[best_gamma_idx]
[…]

### 2022-11-14 src/solutions/q4_and_5.py
plotly update

@@ -176,16 +176,8 @@ def all_parts(
     )
     fig = go.Figure(data=surface)
     fig.update_layout(scene_camera=camera)
-    pio.write_image(fig, contour_path, format='png')
-
-
- #   fig = plt.figure()
-  #  ax = plt.axes(projection="3d")
-   # ax.contour3D(gammas, sigmas, mses)  # type: ignore
-   # ax.set_xlabel("gamma")
-   ## ax.set_ylabel("sigma")
-   # ax.set_zlabel("mse")  # type: ignore
-   # plt.savefig(contour_path)
+    fig.write_image(contour_path)
+   # pio.write_image(fig, contour_path, format='png')
 
     axis_labels += ["GKRR"]
     train_mse, train_std, test_mse, test_std = _regression_report_with_gkrr(
@@ -197,3 +189,4 @@ def all_parts(
         index=["train mse", "train std", "test mse", "test std"],
     ).T
     df.to_csv(report_path)
+

### 2022-11-14 main.py
changed plotting scheme

@@ -146,20 +146,20 @@ if __name__ == "__main__":
         report_path=os.path.join(Q5_OUTPUT_FOLDER, "regression_report.csv"),
     )  # type: ignore
 
-    # Question 6
-    Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
-    if not os.path.exists(Q6_OUTPUT_FOLDER):
-        os.makedirs(Q6_OUTPUT_FOLDER)
-    number_of_points = 100
-    v = 3
-    n_dims = 2
-    q6.all_parts(
-        number_of_points,
-        v,
-        n_dims,
-        figure_title=f"Question 6: h_(S={number_of_points},{v=})",
-        figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
-    )
+    #  # Question 6
+    # Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
+    # if not os.path.exists(Q6_OUTPUT_FOLDER):
+    #     os.makedirs(Q6_OUTPUT_FOLDER)
+    # number_of_points = 100
+    # v = 3
+    # n_dims = 2
+    # q6.all_parts(
+    #     number_of_points,
+    #     v,
+    #     n_dims,
+    #     figure_title=f"Question 6: h_(S={number_of_points},{v=})",
+    #     figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
+    # )
 
     # Question 7
     # Q7_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q7")

### 2022-11-15 main.py
new implementation of linear regression

@@ -4,9 +4,9 @@ import jax
 import numpy as np
 import pandas as pd
 
-from src.constants import OUTPUTS_FOLDER
-from src.models.helpers import phi_polynomial, phi_sin, train_test_split
-from src.solutions import q1, q2_and_3, q4_and_5, q6, q7, q8
+from src.constants import OUTPUTS_FOLDER, DATA_FOLDER
+from src.models.helpers import phi_polynomial, phi_sin, split_train_test_data
+from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
 
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")
@@ -118,48 +118,65 @@ if __name__ == "__main__":
         phi=phi_sin,
     )
 
-    # Question 4 and 5
+    df = pd.read_csv(os.path.join(DATA_FOLDER, "Boston-filtered.csv"))
+    feature_columns = list(df.columns[:-1])
+    target_column = df.columns[-1]
+
+    # Question 4
     Q4_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q4")
-    Q5_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q5")
-
-    if not os.path.exists(Q4_OUTPUT_FOLDER):
-        os.makedirs(Q4_OUTPUT_FOLDER)
-
-    if not os.path.exists(Q5_OUTPUT_FOLDER):
-        os.makedirs(Q5_OUTPUT_FOLDER)
-
-    data = pd.read_csv("data/Boston-filtered.csv")
-    x = np.array(data)
-    x, y = x[:, :-1], x[:, -1]
-    x_train, y_train, x_test, y_test = train_test_split(x, y, 2 / 3)
-
-    q4_and_5.all_parts(
-        x_train,
-        y_train,
-        data_columns=list(data.columns),  # type: ignore
-        figure_title_train="MSE Train",
-        figure_title_test="MSE Test",
-        figure_path_train=os.path.join(Q4_OUTPUT_FOLDER, "q4_train.png"),
-        figure_path_test=os.path.join(Q4_OUTPUT_FOLDER, "q4_test.png"),
-        gkrr_param_path=os.path.join(Q5_OUTPUT_FOLDER, "optimal_gkrr_parameters.csv"),
-        contour_path=os.path.join(Q5_OUTPUT_FOLDER, "contour_plot"),
[…]

### 2022-11-15 src/constants.py

@@ -1,2 +1,4 @@
 OUTPUTS_FOLDER = "outputs"
+DATA_FOLDER = "data"
+
 DEFAULT_SEED = 0

### 2022-11-15 src/models/helpers.py

@@ -1,4 +1,45 @@
+from dataclasses import dataclass
+from typing import List
+
 import numpy as np
+
+
+@dataclass
+class TrainTestData:
+    x_train: np.ndarray
+    y_train: np.ndarray
+    x_test: np.ndarray
+    y_test: np.ndarray
+
+
+def _build_train_test_data(x, y, indices):
+    return TrainTestData(
+        x_train=np.delete(x, indices, axis=0),
+        y_train=np.delete(y, indices, axis=0),
+        x_test=x[indices, :],
+        y_test=y[indices, :],
+    )
+
+
+def split_train_test_data(
+    x: np.ndarray, y: np.ndarray, train_percentage: float
+) -> TrainTestData:
+    n, _ = x.shape
+    train_indices = np.random.choice(np.arange(n), int(train_percentage * n))
+    return _build_train_test_data(x, y, indices=train_indices)
+
+
+def make_folds(
+    x: np.ndarray, y: np.ndarray, number_of_folds: int
+) -> List[TrainTestData]:
+    n, _ = x.shape
+    indices = np.arange(n)
+    np.random.shuffle(indices)
+    split_indices = np.array_split(indices, number_of_folds)
+    return [
+        _build_train_test_data(x, y, indices=split_index)
+        for split_index in split_indices
+    ]
 
 
 def least_square_solution(x: np.ndarray, y: np.ndarray) -> np.ndarray:
@@ -16,10 +57,3 @@ def phi_sin(x: np.ndarray, k: int):
 def mean_squared_error(y_actual: np.ndarray, y_predicted: np.ndarray):
     return np.mean((y_actual - y_predicted) ** 2)
 
-
-def train_test_split(x, y, split):
-    n = x.shape[0]
-    indices = np.random.choice(range(n), int(split * n))
-    mask = np.ones(n, dtype=bool)
-    mask[indices] = False
-    return x[indices, :], y[indices], x[mask, :], y[mask]

### 2022-11-15 src/models/kernels.py

@@ -1,0 +1,23 @@
+from abc import ABC, abstractmethod
+
+import jax.numpy as jnp
+from jax import vmap
+
+
+class Kernel(ABC):
+    @abstractmethod
+    def k(self, x, y):
+        pass
+
+    def compute_gram(self, x, y):
+        return vmap(lambda x_i: vmap(lambda y_i: self.k(x_i, y_i))(y))(x).reshape(
+            x.shape[0], y.shape[0]
+        )
+
+
+class GaussianKernel(Kernel):
+    def __init__(self, sigma):
+        self.sigma = sigma
+
+    def k(self, x, y):
+        return jnp.exp(-((x - y).T @ (x - y)) / (2 * (self.sigma**2)))

### 2022-11-15 src/models/regression.py

@@ -1,0 +1,79 @@
+from abc import ABC, abstractmethod
+
+import numpy as np
+
+from src.models.helpers import least_square_solution
+from src.models.kernels import Kernel
+
+
+class Regression(ABC):
+    def __init__(self):
+        self.w: np.ndarray = None
+
+    @staticmethod
+    def phi(x):
+        pass
+
+    @abstractmethod
+    def fit(self, x: np.ndarray, y: np.ndarray) -> None:
+        """
+        x (n, d)
+        y (n, 1)
+        return (d, 1)
+        """
+        pass
+
+    def predict(self, x: np.ndarray) -> np.ndarray:
+        """
+        x (n, d)
+        """
+        return x @ self.w
+
+
+class NaiveRegression(Regression):
+    def __init__(self):
+        super().__init__()
+
+    @staticmethod
+    def phi(x):
+        return np.ones((x.shape[0], 1))
+
+    def fit(self, x: np.ndarray, y: np.ndarray) -> None:
+        self.w = least_square_solution(self.phi(x), y)
+
+    def predict(self, x: np.ndarray) -> np.ndarray:
+        """
+        x (n, d)
+        """
+        return self.phi(x) @ self.w
+
+
+class LinearRegression(NaiveRegression):
+    def __init__(self):
+        super().__init__()
+
+    @staticmethod
+    def phi(x):
+        return np.concatenate((x, np.ones((x.shape[0], 1))), axis=1)
+
+
+class KernelRidgeRegression(Regression):
+    def __init__(self, kernel: Kernel, gamma: float):
+        self.kernel = kernel
+        self.gamma = gamma
+        self.x_train: np.ndarray = None
+        super().__init__()
+
+    @staticmethod
+    def compute_k_regularised(x, kernel, gamma):
+        n, _ = x.shape
+        return kernel.compute_gram(x, x) + gamma * n * np.eye(n)
+
+    def fit(self, x: np.ndarray, y: np.ndarray) -> None:
+        self.x_train = x
+        self.w = np.linalg.solve(
+            self.compute_k_regularised(x, self.kernel, self.gamma), y
+        )
+
+    def predict(self, x):
+        return self.kernel.compute_gram(x, self.x_train) @ self.w

### 2022-11-15 src/models/regression_models.py

@@ -1,107 +1,0 @@
-from abc import ABC, abstractmethod
-
-import jax.numpy as jnp
-import numpy as np
-from jax import vmap
-
-from src.models.helpers import least_square_solution
-
-
-class RegressionModel(ABC):
-    def __init__(self):
-        self.coefficients = None
-        self.x_train = None
-
-    @abstractmethod
-    def fit(self, x_train, y_train):
-        raise NotImplementedError("Please Implement this method")
-
-    @abstractmethod
-    def predict(self, x_test):
-        raise NotImplementedError("Please Implement this method")
-
-    def fit_predict(self, x_train, y_train, x_test):
-        self.fit(x_train, y_train)
-        return self.predict(x_test)
-
-    def reset(self):
-        self.coefficients = None
-        self.x_train = None
-
-    @staticmethod
-    def add_ones(X):
-        return np.c_[np.ones(X.shape[0]), X]
-
-
-class NaiveLinearRegression(RegressionModel):
-    def __init__(self):
-        self.coefficients = None
-        super().__init__()
-
-    def fit(self, x_train, y_train):
-        self.coefficients = np.mean(y_train)
-
-    def predict(self, x_test):
-        return np.ones(x_test.shape[0]) * self.coefficients
-
-
-class SingleLinearRegression(RegressionModel):
-    def __init__(self, idx):
-        self.coefficients = None
-        self.idx = idx
-        super().__init__()
-
-    def fit(self, x_train, y_train):
-        self.coefficients = least_square_solution(
-            self.add_ones(x_train[:, self.idx]), y_train
-        )
-
-    def predict(self, x_test):
-        return self.add_ones(x_test[:, self.idx]) @ self.coefficients
-
-
-class MultipleLinearRegression(RegressionModel):
-    def __init__(self):
-        self.coefficients = None
-        super().__init__()
-        self.x_train = None
-
-    def fit(self, x_train, y_train):
-        self.coefficients = least_square_solution(self.add_ones(x_train), y_train)
-
-    def predict(self, x_test):
-        return self.add_ones(x_test) @ self.coefficients
-
-
-class GaussianKernelRidgeRegression(RegressionModel):
-    def __init__(self, gamma: float, sigma: float):
-        self.coefficients: np.ndarray = None  # (N_train ,1)
-        self.gamma: float = gamma
-        self.sigma: float = sigma
[…]

### 2022-11-15 src/solutions/q2_and_3.py

@@ -23,6 +23,7 @@ def _g_noisy_samples(number_of_sample_points, sigma):
 def _calculate_mse(
     number_of_sample_points, sigma, number_test_points, number_of_trials, phi, bases
 ):
+    train_mse = np.zeros((number_of_trials, len(bases)))
     test_mse = np.zeros((number_of_trials, len(bases)))
 
     np.random.seed(DEFAULT_SEED)
@@ -42,8 +43,10 @@ def _calculate_mse(
             x_test = np.random.uniform(low=0, high=1, size=(number_test_points, 1))
             y_test_actual = _g(x_test)
             y_test_prediction = np.dot(phi(x_test, base), weights_dict[base])
+            y_train_prediction = np.dot(phi(x_samples, base), weights_dict[base])
+            train_mse[i, j] = mean_squared_error(y_samples_noisy, y_train_prediction)
             test_mse[i, j] = mean_squared_error(y_test_actual, y_test_prediction)
-    return test_mse
+    return train_mse, test_mse
 
 
 def a_i(number_of_sample_points, sigma, figure_title, figure_path):
@@ -117,7 +120,7 @@ def c_and_d(
     figure_path,
     phi,
 ):
-    test_mse = _calculate_mse(
+    train_mse, test_mse = _calculate_mse(
         number_of_sample_points,
         sigma,
         number_test_points,
@@ -126,9 +129,11 @@ def c_and_d(
         bases=ks,
     )
     plt.figure()
-    plt.plot(ks, np.log(np.mean(test_mse, axis=0)))
+    plt.plot(ks, np.log(np.mean(train_mse, axis=0)), label="Train MSE")
+    plt.plot(ks, np.log(np.mean(test_mse, axis=0)), label="Test MSE")
     plt.title(f"{figure_title} ({number_of_trials=})")
     plt.xlabel("Number of Bases (k)")
     plt.xticks(ks)
     plt.ylabel("ln(avg(MSE))")
+    plt.legend()
     plt.savefig(figure_path)

### 2022-11-15 src/solutions/q4.py

@@ -1,0 +1,124 @@
+import numpy as np
+import pandas as pd
+
+from src.models.helpers import mean_squared_error, split_train_test_data
+from src.models.regression import (
+    LinearRegression,
+    NaiveRegression,
+)
+
+PERFORMANCE_COLUMN_NAMES = [
+    "Model",
+    "Train Set MSE Mean",
+    "Train Set MSE Standard Deviation",
+    "Test Set MSE Mean",
+    "Test Set MSE Standard Deviation",
+]
+
+
+def _compute_naive_performance(x, y, train_percentage: float, number_of_runs: int):
+    train_mses = []
+    test_mses = []
+    model = NaiveRegression()
+    for _ in range(number_of_runs):
+        train_test_data = split_train_test_data(x, y, train_percentage)
+        model.fit(train_test_data.x_train, train_test_data.y_train)
+        train_mses.append(
+            mean_squared_error(
+                model.predict(train_test_data.x_train), train_test_data.y_train
+            )
+        )
+        test_mses.append(
+            mean_squared_error(
+                model.predict(train_test_data.x_test), train_test_data.y_test
+            )
+        )
+    return pd.DataFrame(
+        data=[
+            [
+                "Naive Regression",
+                np.mean(train_mses),
+                np.std(train_mses),
+                np.mean(test_mses),
+                np.std(test_mses),
+            ]
+        ],
+        columns=PERFORMANCE_COLUMN_NAMES,
+    )
+
+
+def _compute_linear_performance(
+    x, y, train_percentage: float, number_of_runs: int, model_name: str
+):
+    train_mses = []
+    test_mses = []
+    model = LinearRegression()
+    for _ in range(number_of_runs):
+        train_test_data = split_train_test_data(x, y, train_percentage)
+        model.fit(train_test_data.x_train, train_test_data.y_train)
+        train_mses.append(
+            mean_squared_error(
+                model.predict(train_test_data.x_train), train_test_data.y_train
+            )
+        )
+        test_mses.append(
+            mean_squared_error(
+                model.predict(train_test_data.x_test), train_test_data.y_test
+            )
+        )
+    return pd.DataFrame(
+        data=[
+            [
+                model_name,
+                np.mean(train_mses),
+                np.std(train_mses),
+                np.mean(test_mses),
+                np.std(test_mses),
+            ]
+        ],
+        columns=PERFORMANCE_COLUMN_NAMES,
+    )
+
+
+def compute_q4_performance(
[…]

### 2022-11-15 src/solutions/q5.py

@@ -1,0 +1,178 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from src.models.helpers import (
+    TrainTestData,
+    make_folds,
+    mean_squared_error,
+    split_train_test_data,
+)
+from src.models.kernels import GaussianKernel
+from src.models.regression import KernelRidgeRegression
+from src.solutions.q4 import PERFORMANCE_COLUMN_NAMES
+
+_MODEL_NAME = "Kernel Ridge Regression"
+
+
+def _convert_to_scientific_notation(x: float) -> str:
+    """
+    Convert value to string in scientific notation
+    :param x: value to convert
+    :return: string of x in scientific notation
+    """
+    return "{:.1e}".format(float(x))
+
+
+def _compute_model_performance(train_test_data: TrainTestData, gamma, sigma):
+    kernel = GaussianKernel(sigma=sigma)
+    model = KernelRidgeRegression(kernel, gamma)
+    model.fit(train_test_data.x_train, train_test_data.y_train)
+    return mean_squared_error(
+        model.predict(train_test_data.x_test), train_test_data.y_test
+    )
+
+
+def find_optimal_parameters(x, y, number_of_folds, gammas, sigmas):
+    folds = make_folds(x, y, number_of_folds)
+    mses = np.zeros((len(sigmas), len(gammas), number_of_folds))
+    for i, sigma in enumerate(sigmas):
+        for j, gamma in enumerate(gammas):
+            for k, fold in enumerate(folds):
+                kernel = GaussianKernel(sigma=sigma)
+                model = KernelRidgeRegression(kernel, gamma)
+                model.fit(fold.x_train, fold.y_train)
+                mses[i, j, k] = mean_squared_error(
+                    model.predict(fold.x_test), fold.y_test
+                )
+    average_mses = np.mean(mses, axis=-1)
+    best_sigma_idx, best_gamma_idx = np.unravel_index(
+        average_mses.argmin(), average_mses.shape
+    )
+    return gammas[best_gamma_idx].item(), sigmas[best_sigma_idx].item(), mses
+
+
+def _compute_kernel_ridge_regression_performance(
+    x,
+    y,
+    train_percentage: float,
+    number_of_runs: int,
+    model_name: str,
+    number_of_folds,
+    gammas,
+    sigmas,
+):
+    train_mses = []
+    test_mses = []
+    mses = []
+    for _ in range(number_of_runs):
[…]

### 2022-11-15 submission.tex
add kernel ridge regression results

@@
 \newpage
-        \item Plotting  the natural $\log$ ($\ln$) of the training error versus the polynomial dimension $k = 1, . . . , 18$:
+        \item[(b \& c)] Plotting the $\ln$ of the train and test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
             \begin{figure}[h]
             \centering
-            \includegraphics[scale=0.5]{outputs/q2/q2b}
-            \caption{Training Error of Polynomial Curves}
-            \label{fig:2b}
-            \end{figure}
-
-        \item Plotting the $\ln$ of the test error for a single trial of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
-            \begin{figure}[h]
-            \centering
-            \includegraphics[scale=0.5]{outputs/q2/q2c}
-            \caption{Testing Error of Polynomial Curves (1 trial)}
+            \includegraphics[scale=0.5]{outputs/q2/q2bc}
+            \caption{Training and Testing Error of Polynomial Curves (1 trial)}
             \label{fig:2c}
             \end{figure}
-\newpage
-        \item Plotting the $\ln$ of the test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
+        \item[(d)] Plotting the $\ln$ of the train and test error for 100 trials of 1000 test points versus the polynomial dimension $k = 1, . . . , 18$:
             \begin{figure}[h]
@@
             \includegraphics[scale=0.5]{outputs/q2/q2d}
-            \caption{Testing Error of Polynomial Curves (100 trials)}
+            \caption{Training and Testing Error of Polynomial Curves (100 trials)}
             \label{fig:2d}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/q3/q3b}
-            \caption{Training Error of $\sin$ Curves}
+            \includegraphics[scale=0.5]{outputs/q3/q3bc}
+            \caption{Training and Testing Error of $\sin$ Curves}
             \label{fig:3b}
@@
             \centering
-            \includegraphics[scale=0.5]{outputs/q3/q3c}
-            \caption{Testing Error of $\sin$ Curves (1 trial)}
-            \label{fig:3c}
-            \end{figure}
-            \begin{figure}[h]
-            \centering
             \includegraphics[scale=0.5]{outputs/q3/q3d}
-            \caption{Testing Error of $\sin$ Curves (100 trials)}
+            \caption{Testing and Testing Error of $\sin$ Curves (100 trials)}
             \label{fig:3d}
@@
     \begin{enumerate}
-        \item 
+        \item[(a)]
         We interpret the naive linear regression model using the existing framework for least squares regressors.\\
@@
         \[\implies f(x_{i}) = 1 \times w^{*} = \bar{y}\]\\
-        We split the data using our train test split function, and train naive, single and multiple linear regression models.
-            We repeat this 20 times and report the MSE on training and test sets.\\
+        Our model in this case is essentially always predicting the average housing price in the training data set.
+%        We split the data using our train test split function, and train naive, single and multiple linear regression models.
+%            We repeat this 20 times and report the MSE on training and test sets.\\
 
-        Here are the plots of training and test error:\\
-        \includegraphics[scale=0.5]{outputs/q4/q4_train.png}\\
-        \includegraphics[scale=0.5]{outputs/q4/q4_test.png}\\
+        \item[(b-d)] Here is a table of the training and test mean squared errors:\\
+        \begin{center}
+        \scalebox{0.8} {\begin{tabular}{c|c|c|c|c}%
+         \textbf{Model}&\textbf{Train Mean}&\textbf{Train St. Dev.}&\textbf{Test Mean} &\textbf{Test St. Dev.}% specify table head
+        \csvreader[head to column names]{outputs/q4/performance.csv}{}% use head of csv as column names
+        {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
+        \end{tabular}
+        }
+        \end{center}
     \end{enumerate}
@@
 \item[5.]
-We fit our kernel ridge regressors for each parameter pair over 5 cross validation folds,
-and search for the pair minimising our mean squared error.\\
+%We fit our kernel ridge regressors for each parameter pair over 5 cross validation folds,
+%and search for the pair minimising our mean squared error.\\
 
-Here are the optimal parameters along with the minimal mean squared error:\\
+%Here are the optimal parameters along with the minimal mean squared error:\\
 
-\item The mean squared error for each fitted curve:
+%The mean squared error for each fitted curve:
+%\begin{center}
+%\begin{tabular}{c|c|c}%
+%\textbf{Gamma}&\textbf{Sigma}&\textbf{MSE}% specify table head
+%\csvreader[head to column names]{outputs/q5/optimal_gkrr_parameters.csv}{}% use head of csv as column names
+%{\\\hline\csvcoli&\csvcolii&\csvcoliii}% specify your coloumns here
+%\end{tabular}
+%\end{center}
+%
+%\\
+
+    \begin{enumerate}
+\item[(a)] The optimal parameters:
+
     \begin{center}
-\begin{tabular}{c|c|c}%
-\textbf{Gamma}&\textbf{Sigma}&\textbf{MSE}% specify table head
-\csvreader[head to column names]{outputs/q5/optimal_gkrr_parameters.csv}{}% use head of csv as column names
-{\\\hline\csvcoli&\csvcolii&\csvcoliii}% specify your coloumns here
+    \scalebox{0.8} {\begin{tabular}{c|c|c|c|c}%
+     \textbf{Trial}&$\log_2(\sigma)$&$\log_2(\gamma)$ % specify table head
+    \csvreader[head to column names]{outputs/q5/q5a-optimal-params.csv}{}% use head of csv as column names
+    {\\\hline\csvcolii&\csvcoliii&\csvcoliv}% specify your coloumns here
     \end{tabular}
+    }
     \end{center}
 
-\\
-Here is our contour plot for mse over our parameter grid:\\
+\item[(b)] Displaying the logarithm of the mean 5 fold mean squared error for different parameters for a single trial:\\
 
-\includegraphics[scale = 0.5]{outputs/q5/contour_plot.png}\\
+\begin{centering}
+\includegraphics[scale = 0.5]{outputs/q5/q5b-cross-valid-error}\\
+\end{centering}
+\item[(c)]The mean squared error for the training and test sets for the best $\gamma$ and $\sigma$ for a single trial:
+    \begin{center}
+    \scalebox{0.8} {\begin{tabular}{c|c|c|c|c}%
+     \textbf{Model}&\textbf{Train Mean}&\textbf{Test Mean} % specify table head
+    \csvreader[head to column names]{outputs/q5/q5c-performance.csv}{}% use head of csv as column names
+    {\\\hline\csvcoli&\csvcolii&\csvcoliv}% specify your coloumns here
+    \end{tabular}
+    }
+    \end{center}
 
-\item[5.]
-
-Here is our final regression report over all oour models, run 20 times each.\\
-
-\item The mean squared error for each fitted curve:
+\item[(d)]The mean squared error for each fitted curve over 20 runs:
         \begin{center}
-\begin{tabular}{c|c|c|c|c}%
-\textbd{model}&\textbf{train mse}&\textbf{train std}&\textbf{test mse}&\textbf{test std}% specify table head
-\csvreader[head to column names]{outputs/q5/regression_report.csv}{}% use head of csv as column names
+        \scalebox{0.8} {\begin{tabular}{c|c|c|c|c}%
+         \textbf{Model}&\textbf{Train Mean}&\textbf{Train St. Dev.}&\textbf{Test Mean} &\textbf{Test St. Dev.}% specify table head
+        \csvreader[head to column names]{outputs/q5/q5d-performance.csv}{}% use head of csv as column names
         {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvcoliv&\csvcolv}% specify your coloumns here
         \end{tabular}
+        }
         \end{center}
-
+    \end{enumerate}
+\newpage
 \section{PART II}

### 2022-11-15 main.py

@@ -4,7 +4,7 @@ import jax
 import numpy as np
 import pandas as pd
 
-from src.constants import OUTPUTS_FOLDER, DATA_FOLDER
+from src.constants import OUTPUTS_FOLDER, DATA_FOLDER, DEFAULT_SEED
 from src.models.helpers import phi_polynomial, phi_sin, split_train_test_data
 from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
 
@@ -26,7 +26,7 @@ if __name__ == "__main__":
         x,
         y,
         ks,
-        figure_title="Question 1a: Regression",
+        figure_title="Regression",
         figure_path=os.path.join(Q1_OUTPUT_FOLDER, "q1a.png"),
     )
     q1.b(x, y, ks, table_path=os.path.join(Q1_OUTPUT_FOLDER, "q1b.csv"))
@@ -42,41 +42,33 @@ if __name__ == "__main__":
     q2_and_3.a_i(
         number_of_sample_points,
         sigma,
-        figure_title="Question 2ai: Noisy Samples",
+        figure_title="Noisy Samples",
         figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2ai.png"),
     )
     q2_and_3.a_ii(
         number_of_sample_points,
         sigma,
         ks,
-        figure_title="Question 2aii: Regression with Polynomial Basis",
+        figure_title="Regression with Polynomial Basis",
         figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2aii.png"),
     )
-    q2_and_3.b(
-        number_of_sample_points,
-        sigma,
-        ks=np.arange(1, 19),
-        figure_title="Question 2b: Training Error vs Polynomial Dimension",
-        figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2b.png"),
-        phi=phi_polynomial,
-    )
-    q2_and_3.c_and_d(
+    q2_and_3.bcd(
         number_of_sample_points,
         sigma,
         ks=np.arange(1, 19),
         number_test_points=1000,
         number_of_trials=1,
-        figure_title="Question 2c: Test Error",
-        figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2c.png"),
+        figure_title="Error vs Polynomial Dimension",
+        figure_path=os.path.join(Q2_OUTPUT_FOLDER, "q2bc.png"),
[…]

### 2022-11-15 src/models/helpers.py

@@ -56,4 +56,3 @@ def phi_sin(x: np.ndarray, k: int):
 
 def mean_squared_error(y_actual: np.ndarray, y_predicted: np.ndarray):
     return np.mean((y_actual - y_predicted) ** 2)
-

### 2022-11-15 src/solutions/q2_and_3.py

@@ -88,29 +88,7 @@ def a_ii(
     plt.savefig(figure_path)
 
 
-def b(number_of_sample_points, sigma, ks, figure_title, figure_path, phi):
-    weights = {}
-    x_samples, y_samples_noisy = _g_noisy_samples(number_of_sample_points, sigma)
-    for k in ks:
-        weights[k] = least_square_solution(phi(x_samples, k), y_samples_noisy)
-
-    mse_train = np.array(
-        [
-            mean_squared_error(y_samples_noisy, np.dot(phi(x_samples, k), weights[k]))
-            for k in ks
-        ]
-    )
-
-    plt.figure()
-    plt.plot(ks, np.log(mse_train))
-    plt.title(figure_title)
-    plt.xlabel("Number of Bases (k)")
-    plt.xticks(ks)
-    plt.ylabel("ln(MSE)")
-    plt.savefig(figure_path)
-
-
-def c_and_d(
+def bcd(
     number_of_sample_points,
     sigma,
     number_test_points,

### 2022-11-15 src/solutions/q4.py

@@ -37,10 +37,10 @@ def _compute_naive_performance(x, y, train_percentage: float, number_of_runs: in
         data=[
             [
                 "Naive Regression",
-                np.mean(train_mses),
-                np.std(train_mses),
-                np.mean(test_mses),
-                np.std(test_mses),
+                np.round(np.mean(train_mses), 2),
+                np.round(np.std(train_mses), 2),
+                np.round(np.mean(test_mses), 2),
+                np.round(np.std(test_mses), 2),
             ]
         ],
         columns=PERFORMANCE_COLUMN_NAMES,
@@ -70,10 +70,10 @@ def _compute_linear_performance(
         data=[
             [
                 model_name,
-                np.mean(train_mses),
-                np.std(train_mses),
-                np.mean(test_mses),
-                np.std(test_mses),
+                np.round(np.mean(train_mses), 2),
+                np.round(np.std(train_mses), 2),
+                np.round(np.mean(test_mses), 2),
+                np.round(np.std(test_mses), 2),
             ]
         ],
         columns=PERFORMANCE_COLUMN_NAMES,

### 2022-11-15 src/solutions/q5.py

@@ -33,14 +33,14 @@ def _compute_model_performance(train_test_data: TrainTestData, gamma, sigma):
     )
 
 
-def find_optimal_parameters(x, y, number_of_folds, gammas, sigmas):
-    folds = make_folds(x, y, number_of_folds)
-    mses = np.zeros((len(sigmas), len(gammas), number_of_folds))
-    for i, sigma in enumerate(sigmas):
-        for j, gamma in enumerate(gammas):
+def find_optimal_parameters(x, y, number_of_folds, log_2_gammas, log_2_sigmas):
+    mses = np.zeros((len(log_2_sigmas), len(log_2_gammas), number_of_folds))
+    for i, log_2_sigma in enumerate(log_2_sigmas):
+        for j, log_2_gamma in enumerate(log_2_gammas):
+            folds = make_folds(x, y, number_of_folds)
+            kernel = GaussianKernel(sigma=2.0**log_2_sigma)
+            model = KernelRidgeRegression(kernel, 2.0**log_2_gamma)
             for k, fold in enumerate(folds):
-                kernel = GaussianKernel(sigma=sigma)
-                model = KernelRidgeRegression(kernel, gamma)
                 model.fit(fold.x_train, fold.y_train)
                 mses[i, j, k] = mean_squared_error(
                     model.predict(fold.x_test), fold.y_test
@@ -49,7 +49,11 @@ def find_optimal_parameters(x, y, number_of_folds, gammas, sigmas):
     best_sigma_idx, best_gamma_idx = np.unravel_index(
         average_mses.argmin(), average_mses.shape
     )
-    return gammas[best_gamma_idx].item(), sigmas[best_sigma_idx].item(), mses
+    return (
+        log_2_gammas[best_gamma_idx].item(),
+        log_2_sigmas[best_sigma_idx].item(),
+        mses,
+    )
 
 
 def _compute_kernel_ridge_regression_performance(
@@ -59,24 +63,25 @@ def _compute_kernel_ridge_regression_performance(
     number_of_runs: int,
     model_name: str,
     number_of_folds,
-    gammas,
-    sigmas,
+    log_2_gammas,
+    log_2_sigmas,
 ):
     train_mses = []
     test_mses = []
     mses = []
+    best_log_2_gammas = []
+    best_log_2_sigmas = []
     for _ in range(number_of_runs):
         train_test_data = split_train_test_data(x, y, train_percentage)
-        gamma, sigma, mse = find_optimal_parameters(
[…]

### 2022-11-15 main.py
change random seed for better visualisations

@@ -4,8 +4,8 @@ import jax
 import numpy as np
 import pandas as pd
 
-from src.constants import OUTPUTS_FOLDER, DATA_FOLDER, DEFAULT_SEED
-from src.models.helpers import phi_polynomial, phi_sin, split_train_test_data
+from src.constants import DATA_FOLDER, DEFAULT_SEED, OUTPUTS_FOLDER
+from src.models.helpers import phi_polynomial, phi_sin
 from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
 
 if __name__ == "__main__":
@@ -39,6 +39,7 @@ if __name__ == "__main__":
     number_of_sample_points = 30
     sigma = 0.07
     ks = np.array([2, 5, 10, 14, 18])
+    np.random.seed(DEFAULT_SEED)
     q2_and_3.a_i(
         number_of_sample_points,
         sigma,
@@ -139,94 +140,80 @@ if __name__ == "__main__":
         performance_csv_path=os.path.join(Q5_OUTPUT_FOLDER, "q5c-performance.csv"),
         mse_figure_path=os.path.join(Q5_OUTPUT_FOLDER, "q5b-cross-valid-error.png"),
     )
-    # q5.d(
-    #     df,
-    #     feature_columns,
-    #     target_column,
-    #     train_percentage,
-    #     number_of_runs=20,
-    #     number_of_folds=5,
-    #     log_2_gammas=np.arange(-40, -25),
-    #     log_2_sigmas=np.arange(7, 13.5, 0.5),
-    #     q4_performance_csv_path=q4_performance_csv_path,
-    #     performance_csv_path=os.path.join(Q5_OUTPUT_FOLDER, "q5d-performance.csv"),
-    # )
+    q5.d(
+        df,
+        feature_columns,
+        target_column,
+        train_percentage,
+        number_of_runs=20,
+        number_of_folds=5,
+        log_2_gammas=np.arange(-40, -25),
+        log_2_sigmas=np.arange(7, 13.5, 0.5),
+        q4_performance_csv_path=q4_performance_csv_path,
+        performance_csv_path=os.path.join(Q5_OUTPUT_FOLDER, "q5d-performance.csv"),
+    )
 
-    # # Question 6
-    # Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
-    # if not os.path.exists(Q6_OUTPUT_FOLDER):
-    #     os.makedirs(Q6_OUTPUT_FOLDER)
[…]

### 2022-11-15 src/constants.py

@@ -1,4 +1,4 @@
 OUTPUTS_FOLDER = "outputs"
 DATA_FOLDER = "data"
 
-DEFAULT_SEED = 0
+DEFAULT_SEED = 42

### 2022-11-15 src/solutions/q4.py

@@ -2,10 +2,7 @@ import numpy as np
 import pandas as pd
 
 from src.models.helpers import mean_squared_error, split_train_test_data
-from src.models.regression import (
-    LinearRegression,
-    NaiveRegression,
-)
+from src.models.regression import LinearRegression, NaiveRegression
 
 PERFORMANCE_COLUMN_NAMES = [
     "Model",

### 2022-11-15 src/solutions/q5.py

@@ -155,6 +155,7 @@ def abc(
     average_mses = np.mean(mses[0], axis=-1)
     plt.figure()
     plt.imshow(np.log(average_mses))
+    plt.colorbar()
     plt.xticks(
         np.arange(len(log_2_gammas)),
         labels=log_2_gammas.reshape(-1),

### 2022-11-15 src/models/kernels.py
add linear kernel

@@ -21,3 +21,12 @@ class GaussianKernel(Kernel):
 
     def k(self, x, y):
         return jnp.exp(-((x - y).T @ (x - y)) / (2 * (self.sigma**2)))
+
+
+class LinearKernel(Kernel):
+    def __init__(self, c):
+        self.c = c
+
+    def k(self, x, y):
+        return self.c + x@y
+

### 2022-11-15 main.py
fix bug for text set mse

@@ -168,52 +168,52 @@ if __name__ == "__main__":
         figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
     )
 
-    # Question 7
-    Q7_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q7")
-    if not os.path.exists(Q7_OUTPUT_FOLDER):
-        os.makedirs(Q7_OUTPUT_FOLDER)
-    v = 3
-    n_dims = 2
-    k_values = np.arange(1, 50)
-    number_of_runs = 100
-    number_of_real_points = 100
-    number_of_train_points = 4000
-    number_of_test_points = 1000
-
-    q7.all_parts(
-        k_values,
-        v,
-        n_dims,
-        number_of_runs,
-        number_of_real_points,
-        number_of_train_points,
-        number_of_test_points,
-        figure_title="Question 7: Protocol A",
-        figure_path=os.path.join(Q7_OUTPUT_FOLDER, "q7.png"),
-    )
-
-    # Question 8
-    Q8_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q8")
-    if not os.path.exists(Q8_OUTPUT_FOLDER):
-        os.makedirs(Q8_OUTPUT_FOLDER)
-    v = 3
-    n_dims = 2
-    k_values = np.arange(1, 50)
-    number_of_runs = 100
-    number_of_real_points = 100
-    number_of_train_points_vector = np.concatenate(
-        (np.array([100]), np.arange(500, 4500, 500))
-    )
-    number_of_test_points = 1000
-
-    q8.all_parts(
-        k_values,
-        v,
-        n_dims,
-        number_of_runs,
-        number_of_real_points,
-        number_of_train_points_vector,
-        number_of_test_points,
-        figure_title="Question 8: Protocol B",
-        figure_path=os.path.join(Q8_OUTPUT_FOLDER, "q8.png"),
-    )
+    # # Question 7
+    # Q7_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q7")
+    # if not os.path.exists(Q7_OUTPUT_FOLDER):
+    #     os.makedirs(Q7_OUTPUT_FOLDER)
+    # v = 3
+    # n_dims = 2
+    # k_values = np.arange(1, 50)
+    # number_of_runs = 100
+    # number_of_real_points = 100
+    # number_of_train_points = 4000
+    # number_of_test_points = 1000
[…]

### 2022-11-15 src/solutions/q2_and_3.py

@@ -41,7 +41,7 @@ def _calculate_mse(
             )
         for j, base in enumerate(weights_dict.keys()):
             x_test = np.random.uniform(low=0, high=1, size=(number_test_points, 1))
-            y_test_actual = _g(x_test)
+            y_test_actual = _g_sigma(x_test, sigma)
             y_test_prediction = np.dot(phi(x_test, base), weights_dict[base])
             y_train_prediction = np.dot(phi(x_samples, base), weights_dict[base])
             train_mse[i, j] = mean_squared_error(y_samples_noisy, y_train_prediction)

### 2022-11-15 submission.tex
fixed q9b

@@
         \square$
-    \item Using this kernel in our ridge regression, we arrive at the following prediction function:
-    \\
-    \[\hat{y}_{test} = lc + \sum_{i} \alpha_{i} x_{i} \cdot x_{test} \]
+    \item Using this kernel in our ridge regression, we note that as the value of c increases, the value of the kernel converges to a single value, c. More concretely, the 
+    kernel between any 2 datapoints becomes relatively uniform. We may infer from this that adding a constant in our kernel function has a regularising effect, as the model.\\
+    Expanding on this we demonstrate that we converge to naive linear regression in the limit:\\
 
-    where $\mathbf{\alpha} = ( K + \gamma l I_{l} + c 1_{nxn}) ^{-1} y_{train}$\\
-    Where $1_{nxn}$ is a matrix of all ones.\\
+    Note as $c \to \infty$, $K  = XX^T + C 1_{nxn} \to C 1_{nxn} = C 1_{n} 1_{n}^T$, where $1_{l,m}$ is an lxm dimensional vector a=of all ones.
+Note the similarity here with naive linear regression, where $X =1_{n}$.\\
 
-    We note that as c becomes large, $\alpha \to 0$ and hence the predictions for $\hat{y}_{test}$ approach
-    the constant function $f(x) = lc$\\
+    $\alpha = c^{-1} $leastsquares$(1_{nxn}, y_{train})$ (we no longer assume invertibility)\\
+    $\implies \hat{y}_{test} = c \alpha 1_{n_{train},n_{test}} = 1_{n_{train},n_{test}} $leastsquares$(1_{nxn}, y_{train})$\\
 
-    Hence, adding c to our kernel acts like a regulariser in the limit.\\ 
+     Hence for our predictions, the constants C cancel out and we are left with the exact dual form of naive linear regression:\\
+
+     $\alpha \prime = leastsquares$(1_{nxn}, y_{train}) = \overline{y}_{train}$\\
+     $y_{test} = \alpha \prime 1_{n_{train},n_{test}} = [\overline{y}_{train}]_{1:n_{train}}$
+    Hence,
+    Hence, adding c to our kernel acts like a regulariser.\\ 
 \end{enumerate}

### 2022-11-15 main.py
update jax to 64 bit

@@ -10,6 +10,7 @@ from src.solutions import q1, q2_and_3, q4, q5, q6, q7, q8
 
 if __name__ == "__main__":
     jax.config.update("jax_platform_name", "cpu")
+    jax.config.update("jax_enable_x64", True)
 
     if not os.path.exists(OUTPUTS_FOLDER):
         os.makedirs(OUTPUTS_FOLDER)
@@ -153,20 +154,20 @@ if __name__ == "__main__":
         performance_csv_path=os.path.join(Q5_OUTPUT_FOLDER, "q5d-performance.csv"),
     )
 
-    # Question 6
-    Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
-    if not os.path.exists(Q6_OUTPUT_FOLDER):
-        os.makedirs(Q6_OUTPUT_FOLDER)
-    number_of_points = 100
-    v = 3
-    n_dims = 2
-    q6.all_parts(
-        number_of_points,
-        v,
-        n_dims,
-        figure_title=f"Question 6: h_(S={number_of_points},{v=})",
-        figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
-    )
+    # # Question 6
+    # Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
+    # if not os.path.exists(Q6_OUTPUT_FOLDER):
+    #     os.makedirs(Q6_OUTPUT_FOLDER)
+    # number_of_points = 100
+    # v = 3
+    # n_dims = 2
+    # q6.all_parts(
+    #     number_of_points,
+    #     v,
+    #     n_dims,
+    #     figure_title=f"Question 6: h_(S={number_of_points},{v=})",
+    #     figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
+    # )
 
     # # Question 7
     # Q7_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q7")

### 2022-11-15 src/models/kernels.py

@@ -10,9 +10,11 @@ class Kernel(ABC):
         pass
 
     def compute_gram(self, x, y):
-        return vmap(lambda x_i: vmap(lambda y_i: self.k(x_i, y_i))(y))(x).reshape(
-            x.shape[0], y.shape[0]
-        )
+        return vmap(
+            lambda x_i: vmap(
+                lambda y_i: self.k(x_i, y_i)
+            )(y)
+        )(x)
 
 
 class GaussianKernel(Kernel):

### 2022-11-15 src/models/regression.py

@@ -71,9 +71,9 @@ class KernelRidgeRegression(Regression):
 
     def fit(self, x: np.ndarray, y: np.ndarray) -> None:
         self.x_train = x
-        self.w = np.linalg.solve(
-            self.compute_k_regularised(x, self.kernel, self.gamma), y
-        )
+        self.w = np.linalg.inv(
+            self.compute_k_regularised(x, self.kernel, self.gamma)
+        )@y
 
     def predict(self, x):
         return self.kernel.compute_gram(x, self.x_train) @ self.w

### 2022-11-15 src/solutions/q5.py

@@ -35,9 +35,9 @@ def _compute_model_performance(train_test_data: TrainTestData, gamma, sigma):
 
 def find_optimal_parameters(x, y, number_of_folds, log_2_gammas, log_2_sigmas):
     mses = np.zeros((len(log_2_sigmas), len(log_2_gammas), number_of_folds))
+    folds = make_folds(x, y, number_of_folds)
     for i, log_2_sigma in enumerate(log_2_sigmas):
         for j, log_2_gamma in enumerate(log_2_gammas):
-            folds = make_folds(x, y, number_of_folds)
             kernel = GaussianKernel(sigma=2.0**log_2_sigma)
             model = KernelRidgeRegression(kernel, 2.0**log_2_gamma)
             for k, fold in enumerate(folds):

### 2022-11-15 main.py
uncomment

@@ -154,67 +154,67 @@ if __name__ == "__main__":
         performance_csv_path=os.path.join(Q5_OUTPUT_FOLDER, "q5d-performance.csv"),
     )
 
-    # # Question 6
-    # Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
-    # if not os.path.exists(Q6_OUTPUT_FOLDER):
-    #     os.makedirs(Q6_OUTPUT_FOLDER)
-    # number_of_points = 100
-    # v = 3
-    # n_dims = 2
-    # q6.all_parts(
-    #     number_of_points,
-    #     v,
-    #     n_dims,
-    #     figure_title=f"Question 6: h_(S={number_of_points},{v=})",
-    #     figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
-    # )
+    # Question 6
+    Q6_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q6")
+    if not os.path.exists(Q6_OUTPUT_FOLDER):
+        os.makedirs(Q6_OUTPUT_FOLDER)
+    number_of_points = 100
+    v = 3
+    n_dims = 2
+    q6.all_parts(
+        number_of_points,
+        v,
+        n_dims,
+        figure_title=f"Question 6: h_(S={number_of_points},{v=})",
+        figure_path=os.path.join(Q6_OUTPUT_FOLDER, "q6.png"),
+    )
 
-    # # Question 7
-    # Q7_OUTPUT_FOLDER = os.path.join(OUTPUTS_FOLDER, "q7")
-    # if not os.path.exists(Q7_OUTPUT_FOLDER):
-    #     os.makedirs(Q7_OUTPUT_FOLDER)
-    # v = 3
-    # n_dims = 2
-    # k_values = np.arange(1, 50)
-    # number_of_runs = 100
-    # number_of_real_points = 100
-    # number_of_train_points = 4000
-    # number_of_test_points = 1000
-    #
-    # q7.all_parts(
-    #     k_values,
-    #     v,
-    #     n_dims,
-    #     number_of_runs,
-    #     number_of_real_points,
-    #     number_of_train_points,
-    #     number_of_test_points,
-    #     figure_title="Question 7: Protocol A",
-    #     figure_path=os.path.join(Q7_OUTPUT_FOLDER, "q7.png"),
-    # )
-    #
[…]

### 2022-11-15 submission.tex
minor edits

@@
     \begin{enumerate}
-        \item[(a)]
+        \item[(b)]
         We interpret the naive linear regression model using the existing framework for least squares regressors.\\
@@
 
-        \item[(b-d)] Here is a table of the training and test mean squared errors:\\
+        \item[(a,c,d)] Here is a table of the training and test mean squared errors:\\
         \begin{center}
@@
         So as the number of training points increases, the optimal k would increase to include more of the training points within this same fixed radius.
-        We can see in the plot above that we see this general trend as expected, however there is considerable noise in the trend and so a smoother plot would likely requires more runs.
+        We can see in the plot above that we see this general trend as expected, however there is some noise in the trend and so a smoother plot would likely requires more runs.
     \end{enumerate}
@@
         Our function $K_{c}(\cdot, \cdot)$ is psd iff:\\
-        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R}, {\textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:
+        $\forall \{ u_{i} \}_{1:m} \in \mathcal{R}, {\{\textbf{x}_{j}\}_{1:m} \in \mathcal{R}^{n}$:
 
-        $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) \ge 0 $\\
+        $\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{k},\textbf{x}_{l}) \ge 0 $\\
         We expand our kernel function to give: \\
-        \[\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{u},\textbf{x}_{l}) =  \sum_{n,m} cu_{n} u_{m} + \sum_{n,m} \langle\textbf{x}_{n}, \textbf{x}_{m}\rangle u_{n} u_{m}\]
+        \[\sum_{k,l} u_{k}u_{l}K_{c}(\textbf{x}_{k},\textbf{x}_{l}) =  \sum_{n,m} cu_{n} u_{m} + \sum_{n,m} \langle\textbf{x}_{n}, \textbf{x}_{m}\rangle u_{n} u_{m}\]
 
@@
 
-    Note as $c \to \infty$, $K  = XX^T + C 1_{nxn} \to C 1_{nxn} = C 1_{n} 1_{n}^T$, where $1_{l,m}$ is an lxm dimensional vector a=of all ones.
+    Note as $c \to \infty$, $K  = XX^T + c 1_{nxn} \to c 1_{nxn} = c 1_{n} 1_{n}^T$, where $1_{l,m}$ is an lxm dimensional vector a=of all ones.
 Note the similarity here with naive linear regression, where $X =1_{n}$.\\
@@
 
-     Hence for our predictions, the constants C cancel out and we are left with the exact dual form of naive linear regression:\\
+     Hence for our predictions, the constants c cancel out and we are left with the exact dual form of naive linear regression:\\
 
@@
     Since our operations on a grid are now simply the sum of matrices over a $\mathcal{F}_{2}$, it is now immediately obvious that our operations are commutative, by the commutativity of addition.\\
-
     Further, since applying the same operation twice would be the same as applying the matrix twice in order, we can see that any operation applied twice would have the effect of applying no operation at all ( since $T_{ij} + T_{ij} = 0)$.\\
@@
 From this point, we note that there is no reason for our operations to be square matrices, as the only required properties of the space are those of a vector space (we make no use here of matrix multiplication).
-Hence, we may vectorise both our input grid and our operation matrices to get a set of vectors over $F_{2}^{n^2}$.
+Hence, we may vectorise both our input grid and our operation matrices to get a set of vectors over $\mathcal{F}_{2}^{n^2}$.
 We now index our operation vectors $t_i: i = 1, \dots, n^2$.\\
@@
 Further, gaussian elimination can be performed in $O(n^{3})$ operations in any field, and hence our total running time is $O(n^3)$.
-\\
 

### 2022-11-15 src/models/kernels.py
black

@@ -10,11 +10,7 @@ class Kernel(ABC):
         pass
 
     def compute_gram(self, x, y):
-        return vmap(
-            lambda x_i: vmap(
-                lambda y_i: self.k(x_i, y_i)
-            )(y)
-        )(x)
+        return vmap(lambda x_i: vmap(lambda y_i: self.k(x_i, y_i))(y))(x)
 
 
 class GaussianKernel(Kernel):
@@ -30,5 +26,4 @@ class LinearKernel(Kernel):
         self.c = c
 
     def k(self, x, y):
-        return self.c + x@y
-
+        return self.c + x @ y

### 2022-11-15 src/models/regression.py

@@ -71,9 +71,9 @@ class KernelRidgeRegression(Regression):
 
     def fit(self, x: np.ndarray, y: np.ndarray) -> None:
         self.x_train = x
-        self.w = np.linalg.inv(
-            self.compute_k_regularised(x, self.kernel, self.gamma)
-        )@y
+        self.w = (
+            np.linalg.inv(self.compute_k_regularised(x, self.kernel, self.gamma)) @ y
+        )
 
     def predict(self, x):
         return self.kernel.compute_gram(x, self.x_train) @ self.w
